```{r, echo=FALSE, message=FALSE, warning=FALSE}
here::i_am("report/01_introduction.Rmd")
library(here)
library(knitr)
library(ggplot2)
library(dplyr)
library(sdmTMB)
# here::dr_here()
options(scipen = 100)
```


```{r mean-weights}
# Mean Halibut weight from trawl
halsampledata <- readRDS(here("data/halibut-surv-samples-all.rds")) %>% filter(survey_abbrev == c("SYN WCVI", "SYN QCS"))
# halmeanlength <- mean(halsampledata$length, na.rm = T) # 74 cm seems reasonable
halmeanweightSYN <- mean(halsampledata$weight / 1000, na.rm = T)
# round(halmeanweightSYN, 2)

# Mean Halibut weight from Adam
halmeanweight <- 9.5 # 21 lbs = 9.52 kg 

# Mean Yelloweye weight from trawl
yesampledata <- readRDS(here("data/yelloweye-surv-samples-all.rds")) %>% filter(survey_abbrev == c("SYN WCVI", "SYN QCS"))
yemeanweightSYN <- mean(yesampledata$weight / 1000, na.rm = T)
# round(yemeanweightSYN, 2)

# Mean Yelloweye weight from HBLL
yesampledata <- readRDS(here("data/yelloweye-surv-samples-all.rds")) %>% filter(survey_abbrev == c("HBLL OUT S"))
yemeanweightHBLL <- mean(yesampledata$weight / 1000, na.rm = T)
# round(yemeanweightHBLL, 2)

# Mean Yelloweye weight from Adam
yemeanweight <- 3.2 # 7 lbs =3.18 kg  
```

# Introduction {#sec:introduction}

"Choke" species are species with limited quota that co-occur with species of fishing interest and therefore limit fishing opportunities. 
In British Columbia, Yelloweye Rockfish (*Sebastes ruberrimus*, hereafter: YE) are a known choke species for the Pacific Halibut (*Hippoglossus stenolepis*, hereafter: halibut) fishery [@forrestEvidenceRapidAvoidance2020a].
Five Nations hold Aboriginal rights to a multi-species fishery that includes YE and halibut.
A 2018 court decision, *Ahousaht Indian Band and Nation* v *Canada* outlined the area of each of the Five Nations’ individual Fishing Territories, which combined are referred to as the Court Defined Area (CDA). 
This type of restricted harvest area within a larger management area raises issues regarding how expected catch ratios of choke and target species might vary at finer spatial scales than normally assessed. 
In this report, we explore the potential for spatiotemporal geostatistical models based on fishery-independent survey data to aid in predicting relative catches of YE and halibut within the CDA and in the management area immediately surrounding it (Groundfish Management Unit Area 3CD5A). 

