---
title: "Estimating relative catches of Pacific Halibut and Yelloweye Rockfish off west coast of Vancouver Island"
author: "Philina English"
date: "20/05/2021"
output: html_document
---

```{r message = F}
library(sf)
library(dplyr)
library(ggplot2)
library(sdmTMB)
# Do we need instructions for installing other dependencies like "pbsmapping"?
# devtools::install_github("seananderson/ggsidekick")
library(ggsidekick) # for fourth_root_power_trans and theme_sleek
theme_set(ggsidekick::theme_sleek())
dir.create("data", showWarnings = FALSE)
dir.create("data-generated", showWarnings = FALSE)
dir.create("models", showWarnings = FALSE)
```

# Retrieve HBLL data (on network)

```{r eval=F}
halsetdata <- gfdata::get_survey_sets("Pacific Halibut", ssid = c(36))
saveRDS(halsetdata, "data/halibut-surv-sets.rds")
halhookdata <- gfdata::get_ll_hook_data("Pacific Halibut", ssid = c(36))
saveRDS(halhookdata, "data/halibut-hook-dat36.rds")

yesetdata <- gfdata::get_survey_sets("Yelloweye Rockfish", ssid = c(36))
saveRDS(yesetdata, "data/yelloweye-surv-sets.rds")
yehookdata <- gfdata::get_ll_hook_data("Yelloweye Rockfish", ssid = c(36))
saveRDS(yehookdata, "data/yelloweye-hook-dat36.rds")

blocks <- gfdata::get_survey_blocks(ssid = 36)
saveRDS(blocks, "data/survey-blocks-36.rds")

# I also copied hbll_s_grid.rda from gfplot into "data" folder
# and will need a folder called "shape-files" containing "taaqwiihak_areaVer2.shp"
# download gshhg-shp-2.3.7 from https://www.ngdc.noaa.gov/mgg/shorelines/data/gshhg/latest/ add place in data folder
```


# Prepare HBLL survey data

Load custom functions including one that takes the set data and hook data retrieve for each species and produces a dataframe for use in sdmTMB model. 

```{r echo=F}
# load misc custom functions
source("functions.R")
```

```{r message = F}
model_data_prep <- function(setdata, hookdata) {
  # add in survey blocks
  block_ids <- readRDS("data/survey-blocks-36.rds")
  d <- dplyr::left_join(setdata, block_ids)
  d$block_designation <- as.numeric(d$block_designation)

  # add variables that adjust for hook competiton (not using most of this currently)
  # this code should deal with the issue of 0 baited hooks being observed.
  adjust <- hookdata %>%
    group_by(year, fishing_event_id) %>%
    mutate(total_hooks = count_target_species + count_non_target_species +
      count_bait_only + count_empty_hooks - count_bent_broken) %>%
    mutate(count_bait_only = replace(count_bait_only, which(count_bait_only == 0), 1)) %>%
    mutate(prop_bait_hooks = count_bait_only / total_hooks) %>%
    mutate(hook_adjust_factor = -log(prop_bait_hooks) / (1 - prop_bait_hooks)) %>%
    mutate(expected_catch = round(count_target_species * hook_adjust_factor))

  # find out which events are in hook data but not set data:
  setdiff(hookdata$fishing_event_id, setdata$fishing_event_id)

  hook_adjusted_data <- left_join(setdata, adjust, by = c("fishing_event_id", "year"))

  hook <- hook_adjusted_data %>%
    select(
      survey_series_id, year, fishing_event_id, total_hooks, prop_bait_hooks,
      hook_adjust_factor, expected_catch
    )

  d <- left_join(d, hook, by = c("survey_series_id", "year", "fishing_event_id"))

  d <- d %>%
    select(
      survey_abbrev, year, longitude, latitude, catch_count, hook_count,
      grouping_code, depth_m, block_designation, hook_adjust_factor, prop_bait_hooks
    ) %>%
    mutate(lon = longitude, lat = latitude) %>%
    rename(survey = survey_abbrev, block = block_designation)

  # convert to utms for sdmTMB model
  d_utm <- convert2utm(d, coords = c("lon", "lat"))

  # TODO: Sean, is this next line still appropriate for outside HBLL?
  d_utm <- filter(d_utm, grouping_code > 270 & grouping_code < 330)
  d_utm$depth_log <- log(d_utm$depth_m)
  d_utm$depth_centred <- d_utm$depth_log - mean(d_utm$depth_log)
  d_utm$depth_mean <- mean(d_utm$depth_log)
  d_utm$depth_sd <- sd(d_utm$depth_centred)
  d_utm$depth_scaled <- d_utm$depth_centred / sd(d_utm$depth_centred)
  d_utm$Y_cent <- d_utm$Y - mean(d_utm$Y)
  d_utm$X_cent <- d_utm$X - mean(d_utm$X)

  # add possible offsets
  d_utm$offset <- log(d_utm$hook_count)
  d_utm$area_swept <- d_utm$hook_count * 0.0024384 * 0.009144 * 1000
  d_utm$offset_area_swept <- log(d_utm$area_swept)
  d_utm$offset_area_hook <- log(d_utm$area_swept / d_utm$hook_adjust_factor)

  d_utm
}

# prep halibut
halsetdata <- readRDS("data/halibut-surv-sets.rds") %>% filter(survey_abbrev == "HBLL OUT S")
halhookdata <- readRDS("data/halibut-hook-dat36.rds")

d_hal <- model_data_prep(halsetdata, halhookdata)
saveRDS(d_hal, "data-generated/halibut-surv-36-model-data.rds")

# prep yelloweye
yesetdata <- readRDS("data/yelloweye-rockfish-surv-sets.rds") %>% filter(survey_abbrev == "HBLL OUT S")
yehookdata <- readRDS("data/yelloweye-rockfish-hook-dat36.rds")

d_ye <- model_data_prep(yesetdata, yehookdata)
saveRDS(d_ye, "data-generated/yelloweye-surv-36-model-data.rds")
```

# Make prediction grid

```{r message= F}
# shouldn't matter which species this is based on since the offsets are currently the same for both
d_utm <- readRDS("data-generated/yelloweye-surv-36-model-data.rds")

load("data/hbll_s_grid.rda")

s_grid_utm <- convert2utm(hbll_s_grid$grid, coords = c("X", "Y"))

s_grid_utm$longitude <- hbll_s_grid$grid$X
s_grid_utm$latitude <- hbll_s_grid$grid$Y

s_grid_utm$offset_area_hook <- mean(d_utm$offset_area_hook)
s_grid_utm$offset_area_swept <- mean(d_utm$offset_area_swept)
s_grid_utm$hook_adjust_factor <- mean(d_utm$hook_adjust_factor)
s_grid_utm$hook_count <- 100 # mean(d_utm$hook_count)
s_grid_utm$offset <- log(100)

years <- sort(unique(d_utm$year))
s_grid_utm <- expand_prediction_grid(s_grid_utm, years = years) %>%
  mutate(depth_centred = log(depth) - mean(d_utm$depth_log)) %>%
  mutate(depth_scaled = depth_centred / sd(d_utm$depth_centred))
s_grid_utm <- mutate(s_grid_utm, Y_cent = Y - mean(d_utm$Y))
s_grid_utm <- mutate(s_grid_utm, X_cent = X - mean(d_utm$X))
```


Trim prediction grid to cover full outside S HBLL

```{r}
full_s_grid_utm <- s_grid_utm
full_s_grid_sf <- st_as_sf(full_s_grid_utm, coords = c("longitude", "latitude"))
st_crs(full_s_grid_sf) <- 4326 # set the coordinate reference system
full_s_grid <- sfc_as_cols(full_s_grid_sf, c("longitude", "latitude"))
st_geometry(full_s_grid) <- NULL
```

Trim prediction grid for just area 5A

```{r}
s_5A_grid_utm <- filter(s_grid_utm, latitude < 51.24999 & latitude > 50.5)
s_5A_grid_sf <- st_as_sf(s_5A_grid_utm, coords = c("longitude", "latitude"))
st_crs(s_5A_grid_sf) <- 4326 # set the coordinate reference system
s_5A_grid <- sfc_as_cols(s_5A_grid_sf, c("longitude", "latitude"))
st_geometry(s_5A_grid) <- NULL
```

Split area 3CD into areas inside and outside court defined area (CDA)

```{r message= F}
s_3CD_grid_utm <- filter(s_grid_utm, latitude < 50.5)
s_3CD_grid_sf <- st_as_sf(s_3CD_grid_utm, coords = c("longitude", "latitude"))
st_crs(s_3CD_grid_sf) <- 4326 # set the coordinate reference system
# s_grid_sf

focal_area <- sf::st_read(dsn = "shape-files/taaqwiihak_areaVer2.shp", layer = "taaqwiihak_areaVer2")
focal_area <- sf::st_transform(focal_area, crs = 4326)

intersected <- sf::st_intersects(s_3CD_grid_sf, focal_area)

cda_grid_sf <- s_3CD_grid_sf[which(lengths(intersected) > 0), ]
noncda_grid_sf <- s_3CD_grid_sf[which(lengths(intersected) == 0), ]

cda_grid <- sfc_as_cols(cda_grid_sf, c("longitude", "latitude"))
noncda_grid <- sfc_as_cols(noncda_grid_sf, c("longitude", "latitude"))
st_geometry(cda_grid) <- NULL
st_geometry(noncda_grid) <- NULL
saveRDS(cda_grid, file = "data-generated/cda_grid.rds")
saveRDS(noncda_grid, file = "data-generated/noncda_grid.rds")
```

# Make relatively finescale mesh

```{r }
# again the same grid should work for both species because the sets are identical in both
mesh400kn <- make_mesh(d_utm, c("X", "Y"), n_knots = 400)
plot(mesh400kn)
```

# Pacific Halibut model 

```{r eval = TRUE}
d_hal <- readRDS("data-generated/halibut-surv-36-model-data.rds")
f <- "models/halibut-hook-count-offset-400kn-AR1.rds"
if (!file.exists(f)) {
  m_halibut <- sdmTMB(
    formula = catch_count ~ 0 + as.factor(year) +
      depth_scaled + I(depth_scaled^2) +
      offset,
    data = d_hal,
    spde = mesh400kn,
    ar1_fields = T,
    time = "year",
    silent = FALSE,
    anisotropy = TRUE,
    reml = TRUE,
    family = nbinom2(link = "log")
  )
  saveRDS(m_halibut, file = f)
}
```


```{r}
m_halibut <- readRDS(file = "models/halibut-hook-count-offset-400kn-AR1.rds")
m_halibut
# tidy(m_halibut, "ran_pars", conf.int = TRUE)
```

```{r}
get_diag(m_halibut)
```


# Yelloweye Rockfish model

```{r eval = TRUE}
d_ye <- readRDS("data-generated/yelloweye-surv-36-model-data.rds")

f <- "models/yelloweye-hook-count-offset-400kn-spatial-only.rds"
if (!file.exists(f)) {
  m_ye <- sdmTMB(
    formula = catch_count ~ 0 + as.factor(year) +
      depth_scaled + I(depth_scaled^2) +
      offset,
    data = d_ye,
    spde = mesh400kn,
    time = NULL,
    silent = FALSE,
    anisotropy = TRUE,
    reml = TRUE,
    family = nbinom2(link = "log")
  )
  saveRDS(m_ye, file = f)
}
```


```{r}
m_ye <- readRDS(file = "models/yelloweye-hook-count-offset-400kn-spatial-only.rds")
m_ye
# tidy(m_ye, "ran_pars", conf.int = TRUE)
```

```{r}
get_diag(m_ye)
```

# Halibut catch predictions and index

For CDA only

```{r eval = TRUE}
f <- "data-generated/halibut-predictions-cda.rds"
if (!file.exists(f)) {
  p_hal_cda <- predict(m_halibut, newdata = cda_grid, return_tmb_object = TRUE)
  saveRDS(p_hal_cda, f)
  i_hal_cda <- get_index(p_hal_cda)
  saveRDS(i_hal_cda, "data-generated/halibut-index-cda.rds")
}
```

For 3CD outside CDA

```{r eval = T}
f <- "data-generated/halibut-index-3CD-outside-cda.rds"
if (!file.exists(f)) {
p_hal_noncda <- predict(m_halibut, newdata = noncda_grid, return_tmb_object = TRUE)
saveRDS(p_hal_noncda, "data-generated/halibut-predictions-3CD-outside-cda.rds")

i_hal_noncda <- get_index(p_hal_noncda)
saveRDS(i_hal_noncda, "data-generated/halibut-index-3CD-outside-cda.rds")
}
```

For area 5A 

```{r eval = T}
f <- "data-generated/halibut-index-5A.rds"
if (!file.exists(f)) {
p_hal_5A <- predict(m_halibut, newdata = s_5A_grid, return_tmb_object = TRUE)
saveRDS(p_hal_noncda, "data-generated/halibut-predictions-5A.rds")

i_hal_5A <- get_index(p_hal_5A)
saveRDS(i_hal_5A, "data-generated/halibut-index-5A.rds")
}
```

For entire southern outside HBLL

```{r eval = T}
f <- "data-generated/halibut-index-all-S.rds"
if (!file.exists(f)) {
p_hal_S <- predict(m_halibut, newdata = full_s_grid, return_tmb_object = TRUE)
saveRDS(p_hal_S, "data-generated/halibut-predictions-all-S.rds")

i_hal_S <- get_index(p_hal_S)
saveRDS(i_hal_S, "data-generated/halibut-index-all-S.rds")
}
```


## Plot index of total halibut catch through time

Total catch index for entire court defined area is in red, remainder of southern stock area is in black.

```{r message = F, echo= F}
i_hal <- readRDS("data-generated/halibut-index-all-S.rds")
i_hal_cda <- readRDS("data-generated/halibut-index-cda.rds")
i_hal_noncda <- readRDS("data-generated/halibut-index-3CD-outside-cda.rds")
i_hal_5A <- readRDS("data-generated/halibut-index-5A.rds")

.dat <- bind_rows(
  mutate(i_hal, Area = "HBLL South"),
  mutate(i_hal_5A, Area = "5A"),
  mutate(i_hal_noncda, Area = "HBLL South non-CDA"),
  mutate(i_hal_cda, Area = "CDA")
)
ggplot(.dat, aes(year, est, fill = Area, colour = Area)) +
  geom_line() + 
  geom_ribbon(aes(ymin = lwr, ymax = upr), alpha = 0.4, colour = NA) +
  xlab("Year") +
  ylab("Estimated total fish caught\nif 100 hooks set in all grid cells") +
  coord_cartesian(expand = FALSE, ylim = c(0, max(i_hal$upr) * 1.04)) +
  scale_x_continuous(breaks = seq(1950, 2050, 2)) +
  theme(plot.margin = margin(11/2, r = 11, 11/2, 11/2)) +
  scale_fill_brewer(palette = "Dark2") +
  scale_colour_brewer(palette = "Dark2")
ggsave("figs/halibut-index-by-area.png", width = 7, height = 4, dpi = 400)
```

## Plot estimated halibut catch per 100 hooks through time

Average predicted catch within the entire court defined area is in red, remainder of southern stock area is in black.

```{r message = F, echo= F}
ggplot(i_hal, aes(year, est/nrow(full_s_grid))) +
  # geom_line() + # index for halibut on full HBLL south
  # geom_ribbon(aes(ymin = lwr / nrow(full_s_grid), ymax = upr / nrow(full_s_grid)), alpha = 0.4) +
  geom_line(data = i_hal_cda, aes(year, est / nrow(cda_grid)), colour = "red") +
  geom_ribbon(data = i_hal_cda, aes(year, ymin = lwr / nrow(cda_grid), ymax = upr / nrow(cda_grid)), alpha = 0.4, fill = "red") +
  # geom_line(data = i_hal_5A, aes(year, est / nrow(s_5A_grid)), colour = "blue") +
  # geom_ribbon(data = i_hal_5A, aes(year, ymin = lwr / nrow(s_5A_grid), ymax = upr / nrow(s_5A_grid)), alpha = 0.4, fill = "blue") +
  geom_line(data = i_hal_noncda, aes(year, est / nrow(noncda_grid)),colour = "orange") +
  geom_ribbon(data = i_hal_noncda, aes(ymin = lwr / nrow(noncda_grid), ymax = upr / nrow(noncda_grid)), alpha = 0.4, fill = "orange") +

  xlab("Year") +
  ylab("Average estimated catch per 100 hooks")
  # coord_cartesian(expand = FALSE, ylim = c(0, max(i_hal$upr) * 1.04))
# ggsave("figs/halibut-index-by-area.png", width = 6, height = 4)
```

# Yelloweye Rockfish catch predictions

For CDA only

```{r eval = TRUE}
if (!file.exists("data-generated/yelloweye-spatial-predictions-cda.rds")) {
  p_ye_cda <- predict(m_ye, newdata = cda_grid, return_tmb_object = TRUE)
  saveRDS(p_ye_cda, "data-generated/yelloweye-spatial-predictions-cda.rds")
  
  i_ye_cda <- get_index(p_ye_cda)
  saveRDS(i_ye_cda, "data-generated/yelloweye-spatial-index-cda.rds")
}
```

For 3CD outside CDA

```{r eval = T}
if (!file.exists("data-generated/yelloweye-spatial-index-3CD-outside-cda.rds")) {
  p_ye_noncda <- predict(m_ye, newdata = noncda_grid, return_tmb_object = TRUE)
  saveRDS(p_ye_noncda, "data-generated/yelloweye-spatial-predictions-3CD-outside-cda.rds")

  i_ye_noncda <- get_index(p_ye_noncda)
  saveRDS(i_ye_noncda, "data-generated/yelloweye-spatial-index-3CD-outside-cda.rds")
}
```

For area 5A 

```{r eval = T}
if (!file.exists("data-generated/yelloweye-spatial-index-5A.rds")) {
  p_ye_5A <- predict(m_ye, newdata = s_5A_grid, return_tmb_object = TRUE)
  saveRDS(p_ye_noncda, "data-generated/yelloweye-spatial-predictions-5A.rds")

  i_ye_5A <- get_index(p_ye_5A)
  saveRDS(i_ye_5A, "data-generated/yelloweye-spatial-index-5A.rds")
}
```

For entire southern outside yelloweye stock including CDA

```{r eval = T}
if (!file.exists("data-generated/yelloweye-spatial-index-all-S.rds")) {
  p_ye_S <- predict(m_ye, newdata = full_s_grid, return_tmb_object = TRUE)
  saveRDS(p_ye_S, "data-generated/yelloweye-spatial-predictions-all-S.rds")

  i_ye_S <- get_index(p_ye_S)
  saveRDS(i_ye_S, "data-generated/yelloweye-spatial-index-all-S.rds")
}
```


# Calculate overall proportion of predicted catch in 3CD is inside vs outside CDA

```{r echo= F}
# halibut index was loaded for plots above, so just load yelloweye index
i_ye_cda <- readRDS("data-generated/yelloweye-spatial-index-cda.rds")
i_ye_noncda <- readRDS("data-generated/yelloweye-spatial-index-3CD-outside-cda.rds")

print("What proportion of grid is inside CDA?")
round(nrow(cda_grid) / (nrow(cda_grid) + nrow(noncda_grid)), 2)
```

Pacific Halibut

```{r echo=F}
# print(" PACIFIC HALIBUT")
i_hal_cda2020 <- filter(i_hal_cda, year == 2020)
i_hal_noncda2020 <- filter(i_hal_noncda, year == 2020)

print("What proportion of estimated total catch is inside CDA in 2020?")
round(i_hal_cda2020$est / (i_hal_cda2020$est + i_hal_noncda2020$est), 2)

print("Average estimated catch per 100 hooks inside CDA:")
(i_hal_cda2020$est / nrow(cda_grid))

print("Average estimated catch per 100 hooks outside CDA:")
(i_hal_noncda2020$est / nrow(noncda_grid))
```

Yelloweye Rockfish

```{r echo=F}
# print("YELLOWEYE ROCKFISH")
print("What proportion of estimated total catch is inside CDA?")
round(i_ye_cda$est / (i_ye_cda$est + i_ye_noncda$est), 2)

print("Average estimated catch per 100 hooks inside CDA:")
(i_ye_cda$est / nrow(cda_grid))

print("Average estimated catch per 100 hooks outside CDA:")
(i_ye_noncda$est / nrow(noncda_grid))
```

# Maps

Predictions depicted for HBLL survey grid area that falls within region 3CD. "Court defined area" area is outlined in red. Only 2020 survey catch is included on first two maps, all years of halibut catch are included on the map showing number of Yelloweye Rockfish expected per halibut caught 2020. 

```{r message = F, echo= F}
p_hal <- readRDS("data-generated/halibut-predictions-all-S.rds")
g <- map_predictions(
  pred_data = filter(p_hal$data, year == 2020),
  obs_data = filter(d_hal, year == 2020),
  size_aes = (catch_count / hook_count) * 100
)
# g
dir.create("figs", showWarnings = FALSE)
ggsave("figs/halibut-2020-predictions-S.png", width = 5.5, height = 6, dpi = 400)
```

```{r message = F, echo= F}
g <- map_predictions(
  pred_data = p_hal$data,
  obs_data = d_hal,
  size_aes = (catch_count / hook_count) * 100
) + facet_wrap(~year)
# g
ggsave("figs/halibut-predictions-S.png", width = 8, height = 10, dpi = 200)
```

```{r message = F, echo= F}
p_ye <- readRDS("data-generated/yelloweye-spatial-predictions-all-S.rds")

g <- map_predictions(
  pred_data = filter(p_ye$data, year == 2020),
  obs_data = filter(d_ye, year == 2020),
  size_aes = (catch_count / hook_count) * 100
)
g
dir.create("figs", showWarnings = FALSE)
ggsave("figs/yelloweye-2020-predictions-S.png", width = 5.5, height = 6)
```


```{r message = F, echo= F}
# calculate ratio of yelloweye to halibut
pyd <- p_ye$data %>% rename(ye_est = est)
phd <- p_hal$data %>%
  rename(hal_est = est) %>%
  select(hal_est, X, Y, year)

ratio_df <- left_join(pyd, phd) %>% mutate(halibut = exp(hal_est), yelloweye = exp(ye_est), ye_per_hal = yelloweye / halibut)

g <- map_predictions(
  pred_data = filter(ratio_df, year == 2020),
  obs_data = filter(d_hal, year == 2020),
  fill_aes = ye_per_hal, fill_lab = "Predicted Yelloweye \nper Halibut",
  size_aes = (catch_count / hook_count) * 100,
  size_lab = "Observed halibut\nper 100 hooks"
)
g

dir.create("figs", showWarnings = FALSE)
ggsave("figs/ye-per-halibut-2020-w-hal-catch-S.png", width = 5.5, height = 6)
```

# Other exploratory plots
```{r message=F, echo=F}
p_hal_cda <- readRDS( "data-generated/halibut-predictions-cda.rds")
p_hal_noncda <- readRDS( "data-generated/halibut-predictions-3CD-outside-cda.rds")
p_ye_cda <- readRDS( "data-generated/yelloweye-spatial-predictions-cda.rds")
p_ye_noncda <- readRDS( "data-generated/yelloweye-spatial-predictions-3CD-outside-cda.rds")
py_cda <- p_ye_cda$data %>% rename(ye_est = est)
py_noncda <- p_ye_noncda$data %>% rename(ye_est = est)
ph_cda <- p_hal_cda$data %>%
  rename(hal_est = est) %>%
  select(hal_est, X, Y, year)
ph_noncda <- p_hal_noncda$data %>%
  rename(hal_est = est) %>%
  select(hal_est, X, Y, year)


ratio_cda <- left_join(py_cda, ph_cda) %>% mutate(
  halibut = exp(hal_est), yelloweye = exp(ye_est),
  ye_per_hal = yelloweye / halibut, hal_per_ye = halibut / yelloweye
)
ratio_noncda <- left_join(py_noncda, ph_noncda) %>% mutate(
  halibut = exp(hal_est), yelloweye = exp(ye_est),
  ye_per_hal = yelloweye / halibut, hal_per_ye = halibut / yelloweye
)

ratio_cda <- ratio_cda[order(ratio_cda$halibut, decreasing = T), ] %>% mutate(ordered = row_number())
ratio_noncda <- ratio_noncda[order(ratio_noncda$halibut, decreasing = T), ] %>% mutate(ordered = row_number())

# ggplot(ratio_noncda) +
#   geom_point(aes(yelloweye, halibut), alpha = 0.5) +
#   geom_point(data = ratio_cda, aes(yelloweye, halibut),
#     inherit.aes = F, colour = "red", alpha = 0.5) +
#   coord_cartesian(expand = F) +
#   ylab("Halibut per per 100 hooks") +
#   xlab("Yelloweye per per 100 hooks")

ggplot(ratio_noncda) +
  geom_point(aes(halibut, yelloweye), alpha = 0.5) +
  geom_point(
    data = ratio_cda, aes(halibut, yelloweye),
    inherit.aes = F, colour = "red", alpha = 0.5
  ) +
  coord_cartesian(expand = F) +
  xlab("Halibut per per 100 hooks") +
  ylab("Yelloweye per per 100 hooks")

# ggplot(filter(ratio_noncda, halibut > 5)) +
#   geom_histogram(aes(ye_per_hal)) +
#   geom_histogram(data = filter(ratio_cda, halibut > 5),aes(ye_per_hal), inherit.aes = F, fill = "red") +
#   ylab("Grid cell with estimate of > 5 halibut per 100 hooks") +
#   xlab("Predicted numder of yelloweye per halibut caught")

ggplot(filter(
  ratio_noncda, halibut > 5 # & yelloweye > 0.1
)) +
  geom_histogram(aes(hal_per_ye)) +
  geom_histogram(data = filter(
    ratio_cda, halibut > 5 # & yelloweye > 0.1
  ), aes(hal_per_ye), inherit.aes = F, fill = "red") +
  ylab("Cells with > 5 halibut per 100 hooks") +
  xlab("Estimated numder of halibut per yelloweye caught")
```

### Experiment with accumulation curve
Solid lines are cumulative halibut catch potential for each addition cell fished in decreasing order of predicted halibut abundance.
Dashed lines are the cumulative yelloweye catch that might be anticipated for those same cells.
```{r message = F, echo= F}
ggplot(
  data = ratio_cda,
  aes(x = ordered)
) +
  geom_line(data = ratio_noncda, aes(x = ordered, y = cumsum((halibut))), inherit.aes = FALSE) +
  geom_line(data = ratio_cda, aes(x = ordered, y = cumsum((halibut))), colour = "red", inherit.aes = FALSE) +
  geom_line(data = ratio_noncda, aes(x = ordered, y = cumsum((yelloweye))), lty = 2, inherit.aes = FALSE) +
  geom_line(data = ratio_cda, aes(x = ordered, y = cumsum((yelloweye))), lty = 2, colour = "red", inherit.aes = FALSE) +
  coord_cartesian(expand = F, xlim = c(0, 2500), ylim = c(0, 9000)) +
  ylab("Fish caught") +
  xlab("Number of cells fished (in order of decreasing Halibut abundance)")
```
