---
title: "Estimating relative biomass of Pacific Halibut and Yelloweye Rockfish off west coast of Vancouver Island"
author: "Philina English"
date: "09/06/2021"
output: html_document
---

```{r message = F}
library(sf)
library(dplyr)
library(ggplot2)
library(tidyr)
# remotes::install_github("pbs-assess/sdmTMB", ref = "pc-prior") # for faster models
library(sdmTMB)
# Do we need instructions for installing other dependencies like "pbsmapping"?
# devtools::install_github("seananderson/ggsidekick")
library(ggsidekick) # for fourth_root_power_trans and theme_sleek
theme_set(ggsidekick::theme_sleek())
dir.create("data", showWarnings = FALSE)
dir.create("data-generated", showWarnings = FALSE)
dir.create("models", showWarnings = FALSE)
```

# Retrieve all survey data 
Must be on network.

```{r eval=F}
halsetdata <- gfdata::get_survey_sets("Pacific Halibut")
saveRDS(halsetdata, "data/halibut-surv-sets-all.rds")

yesetdata <- gfdata::get_survey_sets("Yelloweye Rockfish")
saveRDS(yesetdata, "data/yelloweye-surv-sets-all.rds")

# get detailed biological data, I have retrieved data from all surveys in case comparisons between surveys are needed later
yesampledata <- gfdata::get_survey_samples("Yelloweye Rockfish")
saveRDS(yesampledata, "data/yelloweye-surv-samples-all.rds")

halsampledata <- gfdata::get_survey_samples("Pacific Halibut")
saveRDS(halsampledata, "data/halibut-surv-samples-all.rds")

# I also copied ####_grid.rda from gfplot into "data" folder
# and will need a folder called "shape-files" containing "taaqwiihak_areaVer2.shp"
# download gshhg-shp-2.3.7 from https://www.ngdc.noaa.gov/mgg/shorelines/data/gshhg/latest/ add place in data folder
```


# Stitch together trawl and HBLL survey data

Load custom functions including one that takes all the set data and hook data retrieved for each species and produces a dataframe for use in sdmTMB model. 

These models will be of estimated biomass density, so HBLL catch counts are converted to biomass using the mean weight of all fish sampled on the relevant survey (HBLL for yelloweye and WCVI trawl for halibut). 
The HBLL biomass estimate is further divided by the "area swept" calculation I found in a hook competition script (total_hooks * 0.0024384 * 0.009144 * 1000) except that I am using density estimates in kg/ha from the trawl instead of kg/km2, so I am multiplying by 10000 instead of 1000. 
This results in similar, but not identical, value ranges for both surveys, as would be expected given the different habitats they sample. 


```{r echo=F}
# load misc custom functions
source("functions.R")
```

```{r message=F}
model_data_prep <- function(trawldata, hblldata, hookdata, mean_weight) {
  d <- hblldata
  # add variables that adjust for hook competiton
  # this code should deal with the issue of 0 baited hooks being observed
  adjust <- hookdata %>%
    group_by(year, fishing_event_id) %>%
    mutate(total_hooks = count_target_species + count_non_target_species +
      count_bait_only + count_empty_hooks - count_bent_broken) %>%
    mutate(count_bait_only = replace(count_bait_only, which(count_bait_only == 0), 1)) %>%
    mutate(prop_bait_hooks = count_bait_only / total_hooks) %>%
    mutate(hook_adjust_factor = -log(prop_bait_hooks) / (1 - prop_bait_hooks)) %>%
    mutate(expected_catch = (count_target_species * hook_adjust_factor))

  # find out which events are in hook data but not set data:
  setdiff(hookdata$fishing_event_id, hblldata$fishing_event_id)

  hook_adjusted_data <- left_join(hblldata, adjust, by = c("fishing_event_id", "year"))

  hook <- hook_adjusted_data %>%
    select(
      survey_series_id, year, fishing_event_id, total_hooks, prop_bait_hooks,
      hook_adjust_factor, expected_catch
    )

  d <- left_join(d, hook, by = c("survey_series_id", "year", "fishing_event_id"))

  d <- d %>%
    mutate(
      density = expected_catch * mean_weight / (total_hooks * 0.0024384 * 0.009144 * 10000) # guessing that the area swept calc was for km2 so changing 1000 to 10000 should give it in hectares?
    ) %>%
    select(
      survey_abbrev, year, longitude, latitude, fishing_event_id, depth_m, density,
      catch_count, total_hooks, hook_count, expected_catch
    ) %>%
    mutate(lon = longitude, lat = latitude) %>%
    rename(survey = survey_abbrev)

  dt <- trawldata %>%
    mutate(
      density = density_kgpm2 * 10000 # making density of trawl kg per hectare
    ) %>%
    select(
      survey_abbrev, year, longitude, latitude, fishing_event_id, depth_m, density
    ) %>%
    mutate(lon = longitude, lat = latitude) %>%
    rename(survey = survey_abbrev)

  d <- bind_rows(d, dt) %>% filter(depth_m > 1)

  # convert to utms for sdmTMB model
  d_utm <- convert2utm(d, coords = c("lon", "lat"))

  d_utm$depth_log <- log(d_utm$depth_m)
  d_utm$depth_centred <- d_utm$depth_log - mean(d_utm$depth_log)
  d_utm$depth_mean <- mean(d_utm$depth_log)
  d_utm$depth_sd <- sd(d_utm$depth_centred)
  d_utm$depth_scaled <- d_utm$depth_centred / sd(d_utm$depth_centred)
  d_utm$Y_cent <- d_utm$Y - mean(d_utm$Y)
  d_utm$X_cent <- d_utm$X - mean(d_utm$X)

  d_utm
}

# prep halibut
haltrawldata <- readRDS("data/halibut-surv-sets-all.rds") %>% filter(survey_abbrev %in% c("SYN WCVI", "SYN QCS"))
halhblldata <- readRDS("data/halibut-surv-sets-all.rds") %>% filter(survey_abbrev == "HBLL OUT S")
halhookdata <- readRDS("data/halibut-hook-dat36.rds")
halsampledata <- readRDS("data/halibut-surv-samples-all.rds") %>% filter(survey_abbrev == c("SYN WCVI", "SYN QCS"))

# calculate mean weight for all of SYN WCVI
halmeanweight <- mean(halsampledata$weight / 1000, na.rm = T)
# halmeanlength <- mean(halsampledata$length, na.rm = T) # 74 cm seems reasonable
d_hal <- model_data_prep(haltrawldata, halhblldata, hookdata = halhookdata, mean_weight = halmeanweight)
saveRDS(d_hal, "data-generated/halibut-hybrid-model-data.rds")

# prep yelloweye

yetrawldata <- readRDS("data/yelloweye-surv-sets-all.rds") %>% filter(survey_abbrev %in% c("SYN WCVI", "SYN QCS"))
yehblldata <- readRDS("data/yelloweye-surv-sets-all.rds") %>% filter(survey_abbrev == "HBLL OUT S")
yehookdata <- readRDS("data/yelloweye-rockfish-hook-dat36.rds")
yesampledata <- readRDS("data/yelloweye-surv-samples-all.rds") %>% filter(survey_abbrev %in% c("SYN WCVI", "SYN QCS"))

# calculate mean weight for all of HBLL S
yemeanweight <- mean(yesampledata$weight / 1000, na.rm = T)

d_ye <- model_data_prep(yetrawldata, yehblldata, hookdata = yehookdata, mean_weight = yemeanweight)
saveRDS(d_ye, "data-generated/yelloweye-hybrid-model-data.rds")

years <- unique(yehblldata$year)
```

# Make prediction grids

```{r message=F}
# shouldn't matter which species this is based on since the offsets are currently the same for both

## trim trawl data to hbll_s_grid area
load("data/hbll_s_grid.rda")
# max(hbll_s_grid$grid$Y)

d_utm <- readRDS("data-generated/yelloweye-hybrid-model-data.rds") %>%
  filter(latitude < 52.15507) %>%
  filter(year %in% years)
# d_utm2 <- readRDS("data-generated/halibut-hybrid-model-data.rds") %>% filter(latitude < 52.15507)

s_grid_utm <- convert2utm(hbll_s_grid$grid, coords = c("X", "Y")) %>%
  mutate(X = round(X * 100), Y = round(Y * 100)) %>%
  mutate(X = (X / 100), Y = (Y / 100)) # %>% rename(depth_m = depth)

s_grid_utm$longitude <- hbll_s_grid$grid$X
s_grid_utm$latitude <- hbll_s_grid$grid$Y
s_grid_utm$survey <- "HBLL OUT S"
min(s_grid_utm$X)
max(s_grid_utm$X)

# grid <- readRDS("grids/overall-grid.rds") %>% mutate(X = X/100, Y = Y/100)
load("grids/synoptic_grid.rda")
grid <- synoptic_grid %>%
  mutate(
    X = X / 100, Y = Y / 100,
    depth_m = depth
  ) %>%
  select(X, Y, depth_m, survey2 = survey) %>%
  filter(
    X > min(s_grid_utm$X) & X < max(s_grid_utm$X) &
      Y > min(s_grid_utm$Y) & Y < max(s_grid_utm$Y)
  )

grid_utm <- full_join(grid, s_grid_utm, by = c("X", "Y")) %>%
  mutate(depth = ifelse(is.na(depth_m), depth, depth_m), survey = ifelse(is.na(survey), survey2, survey)) %>%
  select(-depth_m, -latitude, -longitude, -survey2)

# plot(grid2$X, grid2$Y)

years <- sort(unique(yehblldata$year))
grid_utm <- expand_prediction_grid(grid_utm, years = years) %>%
  mutate(depth_centred = log(depth) - mean(d_utm$depth_log)) %>%
  mutate(depth_scaled = depth_centred / sd(d_utm$depth_centred))
# grid_utm <- mutate(grid_utm, Y_cent = Y - mean(d_utm$Y))
# grid_utm <- mutate(grid_utm, X_cent = X - mean(d_utm$X))

grid_xy <- grid_utm %>%
  select(X, Y) %>%
  mutate(X = X * 100, Y = Y * 100)
grid_ll <- utm2ll(grid_xy) %>% rename(longitude = X, latitude = Y)

grid_utm <- bind_cols(grid_utm, grid_ll)
```

Trim prediction grid to cover full outside S HBLL

```{r}
full_s_grid_utm <- grid_utm
full_s_grid_sf <- st_as_sf(full_s_grid_utm, coords = c("longitude", "latitude"))
st_crs(full_s_grid_sf) <- 4326 # set the coordinate reference system
full_s_grid <- sfc_as_cols(full_s_grid_sf, c("longitude", "latitude"))
st_geometry(full_s_grid) <- NULL

saveRDS(full_s_grid, file = "data-generated/full_hybrid_grid.rds")
```

Trim prediction grid for just area 5A

```{r}
s_5A_grid_utm <- filter(grid_utm, latitude < 51.24999 & latitude > 50.5) # trims grid to be just area 5A
s_5A_grid_sf <- st_as_sf(s_5A_grid_utm, coords = c("longitude", "latitude"))
st_crs(s_5A_grid_sf) <- 4326 # set the coordinate reference system
s_5A_grid <- sfc_as_cols(s_5A_grid_sf, c("longitude", "latitude"))
st_geometry(s_5A_grid) <- NULL

saveRDS(s_5A_grid, file = "data-generated/hybrid_5A_grid.rds")
```

Split area 3CD into areas inside and outside court defined area (CDA)

```{r message= F}
s_3CD_grid_utm <- filter(grid_utm, latitude < 50.5) # trims grid to be just area 3CD
s_3CD_grid_sf <- st_as_sf(s_3CD_grid_utm, coords = c("longitude", "latitude"))
st_crs(s_3CD_grid_sf) <- 4326 # set the coordinate reference system
# s_grid_sf

focal_area <- sf::st_read(dsn = "shape-files/taaqwiihak_areaVer2.shp", layer = "taaqwiihak_areaVer2")
focal_area <- sf::st_transform(focal_area, crs = 4326)

intersected <- sf::st_intersects(s_3CD_grid_sf, focal_area)

cda_grid_sf <- s_3CD_grid_sf[which(lengths(intersected) > 0), ]
noncda_grid_sf <- s_3CD_grid_sf[which(lengths(intersected) == 0), ]

cda_grid <- sfc_as_cols(cda_grid_sf, c("longitude", "latitude"))
noncda_grid <- sfc_as_cols(noncda_grid_sf, c("longitude", "latitude"))
st_geometry(cda_grid) <- NULL
st_geometry(noncda_grid) <- NULL
saveRDS(cda_grid, file = "data-generated/hybrid_cda_grid.rds")
saveRDS(noncda_grid, file = "data-generated/hybrid_noncda_grid.rds")
```

# Make relatively finescale mesh

```{r }
# again the same grid should work for both species because the sets are identical in both
mesh400kn <- make_mesh(d_utm, c("X", "Y"), n_knots = 400)
plot(mesh400kn)
```

# Pacific Halibut model 

```{r eval = TRUE}
d_hal <- readRDS("data-generated/halibut-hybrid-model-data.rds") %>%
  filter(latitude < 52.15507) %>%
  filter(year %in% years)
f <- "models/halibut-hybrid-model-hbllyrs-400kn-AR1.rds"
if (!file.exists(f)) {
  m_halibut <- sdmTMB(
    formula = density ~ 0 + as.factor(year) + as.factor(survey) +
      depth_scaled + I(depth_scaled^2),
    data = d_hal,
    spde = mesh400kn,
    ar1_fields = T,
    time = "year",
    silent = FALSE,
    anisotropy = TRUE,
    reml = TRUE,
    family = tweedie(link = "log")
  )
  saveRDS(m_halibut, file = f)
}
```

```{r}
m_halibut <- readRDS(file = "models/halibut-hybrid-model-hbllyrs-400kn-AR1.rds")
m_halibut
# tidy(m_halibut, "ran_pars", conf.int = TRUE)
```

```{r}
get_diag(m_halibut)
```


# Yelloweye Rockfish model

```{r eval=TRUE}
d_ye <- readRDS("data-generated/yelloweye-hybrid-model-data.rds") %>%
  filter(latitude < 52.15507) %>%
  filter(year %in% years)

f <- "models/yelloweye-hybrid-400kn-spatial-only-T-hbllyrs.rds"
if (!file.exists(f)) {
  m_ye <- sdmTMB(
    formula = density ~ 0 + as.factor(year) + as.factor(survey) +
      depth_scaled + I(depth_scaled^2),
    data = d_ye,
    spde = mesh400kn,
    spatial_only = T,
    time = "year",
    silent = FALSE,
    anisotropy = TRUE,
    reml = TRUE,
    family = tweedie(link = "log")
  )
  saveRDS(m_ye, file = f)
}
```


```{r}
m_ye <- readRDS(file = "models/yelloweye-hybrid-400kn-spatial-only-T-hbllyrs.rds")
m_ye
# tidy(m_ye, "ran_pars", conf.int = TRUE)
```

```{r}
get_diag(m_ye)
```


# Halibut catch predictions and index

For CDA only (HBLL and trawl grids)

```{r eval = TRUE}
f <- "data-generated/hybrid-halibut-hbllyrs-AR1-index-cda.rds"
if (!file.exists(f)) {
  p_hal_cda <- predict(m_halibut, newdata = cda_grid, return_tmb_object = TRUE)
  saveRDS(p_hal_cda, "data-generated/hybrid-halibut-hbllyrs-AR1-predictions-cda.rds")
  i_hal_cda <- get_index(p_hal_cda, bias_correct = F)
  saveRDS(i_hal_cda, f)
}

ss <- "data-generated/hybrid-halibut-hbllyrs-AR1-index-cda-sim-200.rds"
if (!file.exists(ss)) {
  i_hal_cda2 <- get_all_sims(m_halibut, newdata = cda_grid)
  saveRDS(i_hal_cda2, ss)
}
```

For 3CD outside CDA (HBLL and trawl grids)

```{r eval = T}
f <- "data-generated/hybrid-halibut-hbllyrs-AR1-index-3CD-outside-cda.rds"
if (!file.exists(f)) {
  p_hal_noncda <- predict(m_halibut, newdata = noncda_grid, return_tmb_object = TRUE)
  saveRDS(p_hal_noncda, "data-generated/hybrid-halibut-hbllyrs-AR1-predictions-3CD-outside-cda.rds")

  i_hal_noncda <- get_index(p_hal_noncda, bias_correct = F)
  saveRDS(i_hal_noncda, f)
}

ss <- "data-generated/hybrid-halibut-hbllyrs-AR1-index-3CD-outside-cda-sim-200.rds"
if (!file.exists(ss)) {
  i_hal_noncda2 <- get_all_sims(m_halibut, newdata = noncda_grid)
  saveRDS(i_hal_noncda2, ss)
}
```

For area 5A (HBLL and trawl grids)

```{r eval = T}
f <- "data-generated/hybrid-halibut-hbllyrs-AR1-index-5A.rds"
if (!file.exists(f)) {
  p_hal_5A <- predict(m_halibut, newdata = s_5A_grid, return_tmb_object = TRUE)
  saveRDS(p_hal_noncda, "data-generated/hybrid-halibut-hbllyrs-AR1-predictions-5A.rds")

  i_hal_5A <- get_index(p_hal_5A, bias_correct = F)
  saveRDS(i_hal_5A, f)
}

ss <- "data-generated/hybrid-halibut-hbllyrs-AR1-index-5A-sim-200.rds"
if (!file.exists(ss)) {
  i_hal_5A2 <- get_all_sims(m_halibut, newdata = s_5A_grid)
  saveRDS(i_hal_5A2, ss)
}
```

For entire southern outside HBLL grid including CDA plus the trawl survey area that falls within HBLL bounds.

```{r eval = T}
f <- "data-generated/hybrid-halibut-hbllyrs-AR1-index-all-S.rds"
if (!file.exists(f)) {
  p_hal_S <- predict(m_halibut, newdata = full_s_grid, return_tmb_object = TRUE)
  saveRDS(p_hal_S, "data-generated/hybrid-halibut-hbllyrs-AR1-predictions-all-S.rds")

  i_hal_S <- get_index(p_hal_S, bias_correct = F) # bias_correction not working only for full grid
  saveRDS(i_hal_S, f)
}

ss <- "data-generated/hybrid-halibut-hbllyrs-AR1-index-all-S-sim-200.rds"
if (!file.exists(ss)) {
  i_hal_S2 <- get_all_sims(m_halibut, newdata = full_s_grid)
  saveRDS(i_hal_S2, ss)
}
```

For just southern outside HBLL 

```{r eval = T}
f <- "data-generated/hybrid-halibut-hbllyrs-AR1-index-hbll-S.rds"
if (!file.exists(f)) {
  
  hbll_s_grid <- filter(full_s_grid, survey == "HBLL OUT S")
  
  p_hal_Sb <- predict(m_halibut, newdata = hbll_s_grid, return_tmb_object = TRUE)
  saveRDS(p_hal_Sb, "data-generated/hybrid-halibut-hbllyrs-AR1-predictions-hbll-S.rds")

  i_hal_Sb <- get_index(p_hal_Sb, bias_correct = T) # bias_correction not working only for full grid
  saveRDS(i_hal_Sb, f)
}

ss <- "data-generated/hybrid-halibut-hbllyrs-AR1-index-hbll-S-sim-200.rds"
if (!file.exists(ss)) {
  i_hal_S2b <- get_all_sims(m_halibut, newdata = hbll_s_grid)
  saveRDS(i_hal_S2b, ss)
}
```


## Plot index of total halibut catch through time

Total catch index for entire court defined area is in red, remainder of southern stock area is in black.

```{r message=F, echo=F}
# i_hal <- readRDS("data-generated/halibut-index-all-S.rds")
# i_hal_cda <- readRDS("data-generated/hybrid-halibut-hbllyrs-AR1-index-cda.rds")
# i_hal_noncda <- readRDS("data-generated/hybrid-halibut-hbllyrs-AR1-index-3CD-outside-cda.rds")
# i_hal_5A <- readRDS("data-generated/halibut-index-5A.rds")
i_hal <- readRDS("data-generated/hybrid-halibut-hbllyrs-AR1-index-all-S-sim-200.rds")[[1]]
i_hal_cda <- readRDS("data-generated/hybrid-halibut-hbllyrs-AR1-index-cda-sim-200.rds")[[1]]
i_hal_noncda <- readRDS("data-generated/hybrid-halibut-hbllyrs-AR1-index-3CD-outside-cda-sim-200.rds")[[1]]
i_hal_5A <- readRDS("data-generated/hybrid-halibut-hbllyrs-AR1-index-5A-sim-200.rds")[[1]]
i_hal_hbll <- readRDS("data-generated/hybrid-halibut-hbllyrs-AR1-index-hbll-S-sim-200.rds")[[1]]

.dat <- bind_rows(
  mutate(i_hal, Area = "HBLL South"),
  mutate(i_hal_hbll, Area = "HBLL grid only"),
  mutate(i_hal_5A, Area = "5A"),
  mutate(i_hal_noncda, Area = "non-CDA 3CD"),
  mutate(i_hal_cda, Area = "CDA")
)
.dat$Area <- ordered(.dat$Area, levels = c("CDA", "non-CDA 3CD", "5A", "HBLL South", "HBLL grid only"))
ggplot(.dat, aes(year, est, fill = Area, colour = Area)) +
  geom_line() +
  geom_ribbon(aes(ymin = lwr, ymax = upr), alpha = 0.4, colour = NA) +
  xlab("Year") +
  ylab("Biomass index") +
  # coord_cartesian(expand = FALSE, ylim = c(0, max(i_hal$upr) * 1.04)) +
  # scale_x_continuous(breaks = seq(1950, 2050, 2)) +
  theme(plot.margin = margin(11 / 2, r = 11, 11 / 2, 11 / 2)) +
  scale_fill_brewer(palette = "Set1") +
  scale_colour_brewer(palette = "Set1")
ggsave("figs/hybrid-halibut-hbllyrs-AR1-index-by-area-sim2.png", width = 7, height = 4, dpi = 400)
```

## Plot estimated halibut catch per 100 hooks through time

Average predicted catch within the entire court defined area is in red, remainder of southern stock area is in black.

```{r message = F, echo= F}

i_hal_cda <- readRDS("data-generated/hybrid-halibut-hbllyrs-AR1-index-cda-sim-200.rds")[[1]]
i_hal_noncda <- readRDS("data-generated/hybrid-halibut-hbllyrs-AR1-index-3CD-outside-cda-sim-200.rds")[[1]]

.dat <- bind_rows(
  mutate(i_hal_noncda,
    Area = "non-CDA 3CD",
    est = est / nrow(noncda_grid),
    lwr = lwr / nrow(noncda_grid),
    upr = upr / nrow(noncda_grid)
  ),
  mutate(i_hal_cda,
    Area = "CDA",
    est = est / nrow(cda_grid),
    lwr = lwr / nrow(cda_grid),
    upr = upr / nrow(cda_grid)
  ),
)
ggplot(.dat, aes(year, est)) +
  geom_line(aes(colour = Area)) +
  geom_ribbon(aes(
    ymin = lwr,
    ymax = upr, fill = Area
  ), alpha = 0.4) +
  xlab("Year") +
  ylab("Biomass density (kg/ha)") +
  scale_fill_brewer(palette = "Set1") +
  scale_colour_brewer(palette = "Set1")
ggsave("figs/hybrid-halibut-average-index-by-area.png", width = 7, height = 4, dpi = 400)
```

## Check distribution of simulations
```{r message=F, echo=F, warning=F}
sim_hal_cda <- readRDS("data-generated/hybrid-halibut-hbllyrs-AR1-index-cda-sim-200.rds")[[2]]
sim_hal_noncda <- readRDS("data-generated/hybrid-halibut-hbllyrs-AR1-index-3CD-outside-cda-sim-200.rds")[[2]]

ggplot(sim_hal_cda, aes(as.factor(year), .value)) + geom_violin(colour = "red") + geom_violin(data = sim_hal_noncda, aes(as.factor(year), .value), colour = "blue")

# ## check that the problem is with the predictions... and it seems to be
# sim_p_hal_cda1 <- readRDS("data-generated/halibut-index-cda-sim-200.rds")[[2]]
# sim_p_hal_cda2 <- readRDS("data-generated/halibut-index-cda-sim-200.rds")[[3]]
# sim_p_hal_cda <- bind_cols(sim_p_hal_cda1, as.data.frame(sim_p_hal_cda2)) %>% group_by(year) %>% summarise(V1 = sum(exp(V1)), V2 = sum(exp(V2)), V3 = sum(exp(V3)))
# sim_p_hal_cda
```


# Yelloweye Rockfish catch predictions

For CDA only (HBLL and trawl grids)

```{r eval = TRUE}
f <- "data-generated/hybrid-yelloweye-hbllyrs-spatial-index-cda.rds"
if (!file.exists(f)) {
  p_ye_cda <- predict(m_ye, newdata = cda_grid, return_tmb_object = TRUE)
  saveRDS(p_ye_cda, "data-generated/hybrid-yelloweye-hbllyrs-spatial-predictions-cda.rds")

  i_ye_cda <- get_index(p_ye_cda, bias_correct = F)
  saveRDS(i_ye_cda, f)
}

ss <- "data-generated/hybrid-yelloweye-hbllyrs-spatial-index-cda-sim-200.rds"
if (!file.exists(ss)) {
  i_ye_cda2 <- get_all_sims(m_ye, newdata = cda_grid)
  saveRDS(i_ye_cda2, ss)
}
```

For 3CD outside CDA (HBLL and trawl grids)

```{r eval = T}
f <- "data-generated/hybrid-yelloweye-hbllyrs-spatial-index-3CD-outside-cda.rds"
if (!file.exists(f)) {
  p_ye_noncda <- predict(m_ye, newdata = noncda_grid, return_tmb_object = TRUE)
  saveRDS(p_ye_noncda, "data-generated/hybrid-yelloweye-hbllyrs-spatial-predictions-3CD-outside-cda.rds")

  i_ye_noncda <- get_index(p_ye_noncda, bias_correct = F)
  saveRDS(i_ye_noncda, f)
}

ss <- "data-generated/hybrid-yelloweye-hbllyrs-spatial-index-3CD-outside-cda-sim-200.rds"
if (!file.exists(ss)) {
  i_ye_noncda2 <- get_all_sims(m_ye, newdata = noncda_grid)
  saveRDS(i_ye_noncda2, ss)
}
```

For area 5A (HBLL and trawl grids)

```{r eval = T}
f <- "data-generated/hybrid-yelloweye-hbllyrs-spatial-index-5A.rds"
if (!file.exists(f)) {
  p_ye_5A <- predict(m_ye, newdata = s_5A_grid, return_tmb_object = TRUE)
  saveRDS(p_ye_5A, "data-generated/hybrid-yelloweye-hbllyrs-spatial-predictions-5A.rds")

  i_ye_5A <- get_index(p_ye_5A, bias_correct = F)
  saveRDS(i_ye_5A, f)
}

ss <- "data-generated/hybrid-yelloweye-hbllyrs-spatial-index-5A-sim-200.rds"
if (!file.exists(ss)) {
  i_ye_5A2 <- get_all_sims(m_ye, newdata = s_5A_grid)
  saveRDS(i_ye_5A2, ss)
}
```

For entire southern outside HBLL grid including CDA plus the trawl survey area that falls within HBLL bounds.
This is roughly equivilant to entire southern outside yelloweye stock.  

```{r eval = T}
f <- "data-generated/hybrid-yelloweye-hbllyrs-spatial-index-all-S.rds"
if (!file.exists(f)) {
  p_ye_S <- predict(m_ye, newdata = full_s_grid, return_tmb_object = TRUE)
  saveRDS(p_ye_S, "data-generated/hybrid-yelloweye-hbllyrs-spatial-predictions-all-S.rds")

  i_ye_S <- get_index(p_ye_S, bias_correct = F)
  saveRDS(i_ye_S, f)
}

ss <- "data-generated/hybrid-yelloweye-hbllyrs-spatial-index-all-S-sim-200.rds"
if (!file.exists(ss)) {
  i_ye_S2 <- get_all_sims(m_ye, newdata = full_s_grid)
  saveRDS(i_ye_S2, ss)
}
```

For just southern outside HBLL 

```{r eval = T}
f <- "data-generated/hybrid-yelloweye-hbllyrs-spatial-index-hbll-S.rds"
if (!file.exists(f)) {
  
  hbll_s_grid <- filter(full_s_grid, survey == "HBLL OUT S")
  
  p_ye_Sb <- predict(m_ye, newdata = hbll_s_grid, return_tmb_object = TRUE)
  saveRDS(p_ye_Sb, "data-generated/hybrid-yelloweye-hbllyrs-spatial-predictions-hbll-S.rds")

  i_ye_Sb <- get_index(p_ye_Sb, bias_correct = T) # bias_correction not working only for full grid
  saveRDS(i_ye_Sb, f)
}

ss <- "data-generated/hybrid-yelloweye-hbllyrs-spatial-index-hbll-S-sim-200.rds"
if (!file.exists(ss)) {
  i_ye_S2b <- get_all_sims(m_ye, newdata = hbll_s_grid)
  saveRDS(i_ye_S2b, ss)
}
```

Total catch index for entire court defined area is in red, remainder of southern stock area is in black.

```{r message=F, echo=F}
i_ye <- readRDS("data-generated/hybrid-yelloweye-hbllyrs-spatial-index-all-S-sim-200.rds")[[1]]
i_ye_cda <- readRDS("data-generated/hybrid-yelloweye-hbllyrs-spatial-index-cda-sim-200.rds")[[1]]
i_ye_noncda <- readRDS("data-generated/hybrid-yelloweye-hbllyrs-spatial-index-3CD-outside-cda-sim-200.rds")[[1]]
i_ye_5A <- readRDS("data-generated/hybrid-yelloweye-hbllyrs-spatial-index-5A-sim-200.rds")[[1]]

i_ye_hbll <- readRDS("data-generated/hybrid-yelloweye-hbllyrs-spatial-index-hbll-S-sim-200.rds")[[1]]

.dat <- bind_rows(
  mutate(i_ye, Area = "HBLL South"),
  mutate(i_ye_hbll, Area = "HBLL grid only"),
  mutate(i_ye_5A, Area = "5A"),
  mutate(i_ye_noncda, Area = "non-CDA 3CD"),
  mutate(i_ye_cda, Area = "CDA")
)
.dat$Area <- ordered(.dat$Area, levels = c("CDA", "non-CDA 3CD", "5A", "HBLL South", "HBLL grid only"))
ggplot(.dat, aes(year, est, fill = Area, colour = Area)) +
  geom_line() +
  geom_ribbon(aes(ymin = lwr, ymax = upr), alpha = 0.4, colour = NA) +
  # geom_line(data = .dat1, linetype = 2) +
  xlab("Year") +
  ylab("Biomass index") +
  coord_cartesian(expand = FALSE, ylim = c(0, max(i_ye$upr) * 1.04)) +
  scale_x_continuous(breaks = seq(1950, 2050, 2)) +
  theme(plot.margin = margin(11 / 2, r = 11, 11 / 2, 11 / 2)) +
  scale_fill_brewer(palette = "Set1") +
  scale_colour_brewer(palette = "Set1")
ggsave("figs/hybrid-yelloweye-hbllyrs-index-by-area.png", width = 7, height = 4, dpi = 400)
```

## Plot estimated halibut catch per 100 hooks through time

Average predicted catch within the entire court defined area is in red, remainder of southern stock area is in black.

```{r message = F, echo= F}
.dat <- bind_rows(
  mutate(i_ye_noncda,
    Area = "non-CDA 3CD",
    est = est / nrow(noncda_grid),
    lwr = lwr / nrow(noncda_grid),
    upr = upr / nrow(noncda_grid)
  ),
  mutate(i_ye_cda,
    Area = "CDA",
    est = est / nrow(cda_grid),
    lwr = lwr / nrow(cda_grid),
    upr = upr / nrow(cda_grid)
  ),
)
ggplot(.dat, aes(year, est)) +
  geom_line(aes(colour = Area)) +
  geom_ribbon(aes(
    ymin = lwr,
    ymax = upr, fill = Area
  ), alpha = 0.4) +
  xlab("Year") +
  ylab("Biomass density (kg/ha)") +
  scale_fill_brewer(palette = "Set1") +
  scale_colour_brewer(palette = "Set1")
ggsave("figs/hybrid-yelloweye-hbllyrs-average-index-by-area.png", width = 7, height = 4, dpi = 400)
```


# Calculate predicted catch rates in different areas

```{r}
i_hal2 <- readRDS("data-generated/hybrid-halibut-hbllyrs-AR1-index-all-S-sim-200.rds")[[2]]
i_hal_cda2 <- readRDS("data-generated/hybrid-halibut-hbllyrs-AR1-index-cda-sim-200.rds")[[2]]
i_hal_noncda2 <- readRDS("data-generated/hybrid-halibut-hbllyrs-AR1-index-3CD-outside-cda-sim-200.rds")[[2]]
i_hal_5A2 <- readRDS("data-generated/hybrid-halibut-hbllyrs-AR1-index-5A-sim-200.rds")[[2]]

.dat2 <- bind_rows(
  mutate(i_hal2, Area = "HBLL South", num_cells = nrow(full_s_grid)),
  mutate(i_hal_5A2, Area = "5A", num_cells = nrow(s_5A_grid)),
  mutate(i_hal_noncda2, Area = "non-CDA 3CD", num_cells = nrow(noncda_grid)),
  mutate(i_hal_cda2, Area = "CDA", num_cells = nrow(cda_grid))
)
.dat2$Area <- ordered(.dat2$Area, levels = c("CDA", "non-CDA 3CD", "5A", "HBLL South"))

i_hal_2020 <- filter(.dat2, year == 2020) %>% filter(.iteration <= 200)

catch_per_cell <- i_hal_2020 %>%
  group_by(Area) %>%
  summarise(
    catch = mean(.value / num_cells),
    catch_med = median(.value / num_cells),
    catch_lwr = quantile(.value / num_cells, 0.025),
    catch_upr = quantile(.value / num_cells, 0.975)
  )

saveRDS(catch_per_cell, "hal_catch_per_cell.rds")
```

```{r}
i_ye2 <- readRDS("data-generated/hybrid-yelloweye-hbllyrs-spatial-index-all-S-sim-200.rds")[[2]]
i_ye_cda2 <- readRDS("data-generated/hybrid-yelloweye-hbllyrs-spatial-index-cda-sim-200.rds")[[2]]
i_ye_noncda2 <- readRDS("data-generated/hybrid-yelloweye-hbllyrs-spatial-index-3CD-outside-cda-sim-200.rds")[[2]]
i_ye_5A2 <- readRDS("data-generated/hybrid-yelloweye-hbllyrs-spatial-index-5A-sim-200.rds")[[2]]

.dat2 <- bind_rows(
  mutate(i_ye2, Area = "HBLL South", num_cells = nrow(full_s_grid)),
  mutate(i_ye_5A2, Area = "5A", num_cells = nrow(s_5A_grid)),
  mutate(i_ye_noncda2, Area = "non-CDA 3CD", num_cells = nrow(noncda_grid)),
  mutate(i_ye_cda2, Area = "CDA", num_cells = nrow(cda_grid))
)
.dat2$Area <- ordered(.dat2$Area, levels = c("CDA", "non-CDA 3CD", "5A", "HBLL South"))

i_ye_2020 <- filter(.dat2, year == 2020) %>% filter(.iteration <= 200)

ye_catch_per_cell <- i_ye_2020 %>%
  group_by(Area) %>%
  summarise(
    catch = mean(.value / num_cells),
    catch_med = median(.value / num_cells),
    catch_lwr = quantile(.value / num_cells, 0.025),
    catch_upr = quantile(.value / num_cells, 0.975)
  )

saveRDS(ye_catch_per_cell, "ye_catch_per_cell.rds")
```


```{r message=F, echo=F}
ggplot(i_hal_2020) + geom_histogram(aes(.value / num_cells), alpha = 0.75, fill = "black") +
  geom_histogram(data = i_ye_2020, aes(.value / num_cells, fill = Area), alpha = 0.75) +
  geom_vline(data = catch_per_cell, aes(xintercept = catch), linetype = 2, alpha = 0.5, colour = "black") +
  geom_vline(data = ye_catch_per_cell, aes(xintercept = catch, colour = Area), linetype = 2) +
  facet_grid(rows = vars(Area)) + xlab("Mean kg/ha") + ylab("Number of simulations") +
  scale_fill_brewer(palette = "Set1") + scale_colour_brewer(palette = "Set1") + theme(legend.position = "none") +
  ggtitle("Estimated relative biomass densities (mean and distribution)",
    subtitle = "Yelloweye Rockfish (coloured bars) vs. Pacific Halibut (grey bars)"
  )

ggsave("figs/hybrid-estimated-biomass-densities-sim.png", width = 5, height = 5, dpi = 400)
```


# What proportion of estimated total catch is inside CDA in 2020?

What proportion of 3CD HBLL + trawl survey grid is inside CDA?
```{r echo=F}
round(nrow(cda_grid) / (nrow(cda_grid) + nrow(noncda_grid)), 2)
```

```{r echo=F, message=F, warning=F}
hal_ratios <- i_hal_2020 %>%
  select(-num_cells) %>%
  pivot_wider(names_from = Area, values_from = .value) %>%
  group_by(.iteration) %>%
  mutate(CDAto3CD = CDA / (CDA + `non-CDA 3CD`), CDAto3CD5A = CDA / (CDA + `non-CDA 3CD` + `5A`))

mean_hal_ratios <- hal_ratios %>%
  pivot_longer(cols = c(CDAto3CD, CDAto3CD5A), names_to = "area", values_to = "ratio") %>%
  group_by(area) %>%
  summarise(
    ratio = mean(ratio),
    ratio_med = median(ratio),
    ratio_lwr = quantile(ratio, 0.025),
    ratio_upr = quantile(ratio, 0.975)
  )
saveRDS(mean_hal_ratios, "mean_hal_ratios.rds")

ggplot(hal_ratios) +
  geom_histogram(aes(CDAto3CD), fill = "red", alpha = 0.75) +
  geom_histogram(aes(CDAto3CD5A), fill = "black", alpha = 0.5) +
  geom_vline(data = mean_hal_ratios, aes(xintercept = ratio), linetype = 2) +
  xlim(0, max(hal_ratios$CDAto3CD)) +
  xlab("Proportion of total catch inside CDA") + ylab("Number of simulations") +
  ggtitle("Pacific Halibut survey biomass in area 3CD (red) and 3CD + 5A (grey)")
ggsave("figs/hybrid-halibut-relative-biomass-sim.png", width = 7, height = 3, dpi = 400)
```

```{r echo=F, message=F, warning=F}
ye_ratios <- i_ye_2020 %>%
  select(-num_cells) %>%
  pivot_wider(names_from = Area, values_from = .value) %>%
  group_by(.iteration) %>%
  mutate(CDAto3CD = CDA / (CDA + `non-CDA 3CD`), CDAto3CD5A = CDA / (CDA + `non-CDA 3CD` + `5A`))

mean_ye_ratios <- ye_ratios %>%
  pivot_longer(cols = c(CDAto3CD, CDAto3CD5A), names_to = "area", values_to = "ratio") %>%
  group_by(area) %>%
  summarise(
    ratio = mean(ratio),
    ratio_med = median(ratio),
    ratio_lwr = quantile(ratio, 0.025),
    ratio_upr = quantile(ratio, 0.975)
  )
saveRDS(mean_ye_ratios, "mean_ye_ratios.rds")

ggplot(ye_ratios) +
  geom_histogram(aes(CDAto3CD), fill = "red", alpha = 0.75) +
  geom_histogram(aes(CDAto3CD5A), fill = "black", alpha = 0.5) +
  geom_vline(data = mean_ye_ratios, aes(xintercept = ratio), linetype = 2) +
  xlim(0, max(hal_ratios$CDAto3CD)) +
  xlab("Proportion of total biomass inside CDA") + ylab("Number of simulations") +
  ggtitle("Yelloweye Rockfish survey biomass in area 3CD (red) and 3CD + 5A (grey)")
ggsave("figs/hybrid-yelloweye-hbllyrs-relative-biomass-sim.png", width = 7, height = 3, dpi = 400)
```


### Plot ratio of yelloweye to halibut through time
```{r message=F, echo=F, warning=F}
.i_ye <- bind_rows(
  mutate(i_ye2, Area = "HBLL South", num_cells = nrow(full_s_grid)),
  mutate(i_ye_5A2, Area = "5A", num_cells = nrow(s_5A_grid)),
  mutate(i_ye_noncda2, Area = "non-CDA 3CD", num_cells = nrow(noncda_grid)),
  mutate(i_ye_cda2, Area = "CDA", num_cells = nrow(cda_grid))
) %>%
  rename(yelloweye = .value) %>%
  filter(.iteration <= 200)
.i_ye$Area <- ordered(.i_ye$Area, levels = c("CDA", "non-CDA 3CD", "5A", "HBLL South"))

.i_hal <- bind_rows(
  mutate(i_hal2, Area = "HBLL South", num_cells = nrow(full_s_grid)),
  mutate(i_hal_5A2, Area = "5A", num_cells = nrow(s_5A_grid)),
  mutate(i_hal_noncda2, Area = "non-CDA 3CD", num_cells = nrow(noncda_grid)),
  mutate(i_hal_cda2, Area = "CDA", num_cells = nrow(cda_grid))
) %>%
  rename(halibut = .value) %>%
  filter(.iteration <= 200)
.i_hal$Area <- ordered(.i_hal$Area, levels = c("CDA", "non-CDA 3CD", "5A", "HBLL South"))

.dat <- left_join(.i_ye, .i_hal) %>%
  group_by(Area, year) %>%
  summarise(
    ye_per_hal = mean(yelloweye / halibut),
    lwr = quantile(yelloweye / halibut, 0.025),
    upr = quantile(yelloweye / halibut, 0.975)
  ) 

saveRDS(.dat, "ratio-yelloweye-to-halibut.rds")

.dat <- .dat %>% filter(Area %in% c("non-CDA 3CD", "CDA"))

ggplot(.dat, aes(year, ye_per_hal, fill = Area, colour = Area)) +
  geom_line() +
  geom_ribbon(aes(ymin = lwr, ymax = upr), alpha = 0.4, colour = NA) +
  xlab("Year") +
  ylab("Estimated yelloweye to halibut biomass ratio") +
  coord_cartesian(expand = FALSE, ylim = c(0, max(.dat$upr) * 1.04)) +
  scale_x_continuous(breaks = seq(1950, 2050, 2)) +
  theme(plot.margin = margin(11 / 2, r = 11, 11 / 2, 11 / 2)) +
  scale_fill_brewer(palette = "Set1") +
  scale_colour_brewer(palette = "Set1")
ggsave("figs/hybrid-ye-to-hal-index-by-area.png", width = 7, height = 4, dpi = 400)
```


# Check predictions against those from the HBLL only count model
```{r}
hybrid_pred <- readRDS("data-generated/hybrid-halibut-hbllyrs-AR1-predictions-hbll-S.rds")
poisson_pred <- readRDS("data-generated/halibut-predictions-all-S.rds")

hyb <- hybrid_pred$data %>% 
  # mutate(est = exp(est)) %>%
  select(X, Y, year, log_biomass = est)

pois <- poisson_pred$data %>% 
  # mutate(est_exp = exp(est)) %>%
  mutate(X = round(X*100)/100, Y = round(Y*100)/100) %>% 
  select(X, Y, year, log_count = est)

d_test <- left_join(hyb, pois)

ggplot(d_test, aes(log_count, log_biomass)) + geom_point(alpha = 0.1) + facet_wrap(~year)
```

```{r}
hybrid_pred <- readRDS("data-generated/hybrid-yelloweye-hbllyrs-spatial-predictions-hbll-S.rds")
poisson_pred <- readRDS("data-generated/yelloweye-spatial-predictions-all-S.rds")

hyb <- hybrid_pred$data %>% 
  # mutate(est = exp(est)) %>%
  select(X, Y, year, log_biomass = est)

pois <- poisson_pred$data %>% 
  # mutate(est_exp = exp(est)) %>%
  mutate(X = round(X*100)/100, Y = round(Y*100)/100) %>% 
  select(X, Y, year, log_count = est)

d_test <- left_join(hyb, pois)

ggplot(d_test, aes(log_count, log_biomass)) + geom_point(alpha = 0.1) + facet_wrap(~year)
```


# Maps

Predictions depicted for HBLL survey grid area that falls within region 3CD. "Court defined area" area is outlined in red. Only 2020 survey catch is included on first two maps, all years of halibut catch are included on the map showing number of Yelloweye Rockfish expected per halibut caught 2020. 

```{r message=F, echo=F}
p_hal2020 <- readRDS("data-generated/hybrid-halibut-hbllyrs-AR1-predictions-all-S.rds")[[1]] %>% filter(year == 2020)
g <- map_predictions(
  pred_data = p_hal2020,
  obs_data = filter(d_hal, year == 2020),
  fill_lab = "Predicted kg/ha",
  # pred_min = min(exp(p_hal2020$est), na.rm = T),
  # pred_max = quantile(exp(p_hal2020$est), 0.99, na.rm = T),
  size_aes = (catch_count / hook_count) * 100
)
g
dir.create("figs", showWarnings = FALSE)
ggsave("figs/hybrid-halibut-hbllyrs-AR1-2020-predictions-S.png", width = 5.5, height = 6, dpi = 400)
```

```{r map-predictions-all, message=F, echo=F, warning=F, cache=TRUE}
p_hal <- readRDS("data-generated/hybrid-halibut-hbllyrs-AR1-predictions-all-S.rds")
years <- unique(p_hal$data$year)
p_hal_d <- p_hal$data %>%
  filter(year %in% years) %>%
  mutate(year = as.factor(year))
p_hal_d$year <- droplevels(p_hal_d$year)

d_hal <- d_hal %>%
  filter(year %in% years) %>%
  mutate(year = as.factor(year))
d_hal$year <- droplevels(as.factor(d_hal$year))

g <- map_predictions(
  pred_data = p_hal_d,
  pred_min = min(exp(p_hal_d$est), na.rm = T),
  pred_max = quantile(exp(p_hal_d$est), 0.99, na.rm = T),
  obs_data = d_hal,
  fill_lab = "Predicted kg/ha",
  size_aes = (catch_count / hook_count) * 100,
  legend_position = "right"
) + facet_wrap(~ as.factor(year))

# g <- g + theme(legend.position = c(0.35, 0), legend.justification = c(0,0))

ggsave("figs/hybrid-halibut-hbllyrs-AR1-predictions-S2.png", width = 9, height = 10, dpi = 200)
```

```{r message=F, echo=F}
p_ye <- readRDS("data-generated/hybrid-yelloweye-hbllyrs-spatial-predictions-all-S.rds")

g <- map_predictions(
  pred_data = filter(p_ye$data, year == 2020),
  obs_data = filter(d_ye, year == 2020),
  size_aes = (catch_count / hook_count) * 100
)
g
dir.create("figs", showWarnings = FALSE)
ggsave("figs/hybrid-yelloweye-2020-predictions-S.png", width = 5.5, height = 6, dpi = 400)
```


```{r message=F, echo=F}
# calculate ratio of yelloweye to halibut
p_ye <- readRDS("data-generated/hybrid-yelloweye-hbllyrs-spatial-predictions-all-S.rds")
p_hal <- readRDS("data-generated/hybrid-halibut-hbllyrs-AR1-predictions-all-S.rds")
pyd <- p_ye$data %>% rename(ye_est = est)
phd <- p_hal$data %>%
  rename(hal_est = est) %>%
  select(hal_est, X, Y, year)

ratio_df <- left_join(pyd, phd) %>% mutate(halibut = exp(hal_est), yelloweye = exp(ye_est), ye_per_hal = yelloweye / halibut)

g <- map_predictions(
  pred_data = filter(ratio_df, year == 2020),
  obs_data = filter(d_hal, year == 2020),
  fill_aes = ye_per_hal, fill_lab = "Yelloweye\nto Halibut\nbiomass ratio",
  size_aes = (catch_count / hook_count) * 100,
  size_lab = "Halibut caught\nper 100 hooks"
)
g

dir.create("figs", showWarnings = FALSE)
ggsave("figs/hybrid-ye-to-halibut-2020-w-hal-catch-S.png", width = 5.5, height = 6, dpi = 400)
```

Raw data

```{r ye-map-all, cache=TRUE, echo=F, message=F, warning=F}
g <- map_predictions(
  pred_data = p_ye$data,
  obs_data = d_ye,
  fill_lab = "Predicted kg/ha",
  pred_min = min(exp(p_ye$data$est), na.rm = T),
  pred_max = quantile(exp(p_ye$data$est), 0.99, na.rm = T),
  size_aes = (catch_count / hook_count) * 100,
  legend_position = "right"
) + facet_wrap(~year)
# g <- g + theme(legend.position = c(0.35, 0), legend.justification = c(0,0))
ggsave("figs/hybrid-ye-predictions-S.png", width = 9, height = 10, dpi = 200)
```

# Other exploratory plots
```{r message=F, echo=F}
p_hal_cda <- readRDS("data-generated/hybrid-halibut-hbllyrs-AR1-predictions-cda.rds")
p_hal_noncda <- readRDS("data-generated/hybrid-halibut-hbllyrs-AR1-predictions-3CD-outside-cda.rds")
p_ye_cda <- readRDS("data-generated/hybrid-yelloweye-hbllyrs-spatial-predictions-cda.rds")
p_ye_noncda <- readRDS("data-generated/hybrid-yelloweye-hbllyrs-spatial-predictions-3CD-outside-cda.rds")
py_cda <- p_ye_cda$data %>% rename(ye_est = est)
py_noncda <- p_ye_noncda$data %>% rename(ye_est = est)
ph_cda <- p_hal_cda$data %>%
  rename(hal_est = est) %>%
  select(hal_est, X, Y, year)
ph_noncda <- p_hal_noncda$data %>%
  rename(hal_est = est) %>%
  select(hal_est, X, Y, year)


ratio_cda <- left_join(py_cda, ph_cda) %>% mutate(
  halibut = exp(hal_est), yelloweye = exp(ye_est),
  ye_per_hal = yelloweye / halibut, hal_per_ye = halibut / yelloweye
)
ratio_noncda <- left_join(py_noncda, ph_noncda) %>% mutate(
  halibut = exp(hal_est), yelloweye = exp(ye_est),
  ye_per_hal = yelloweye / halibut, hal_per_ye = halibut / yelloweye
)

ratio_cda <- ratio_cda[order(ratio_cda$halibut, decreasing = T), ] %>% mutate(ordered = row_number())
ratio_noncda <- ratio_noncda[order(ratio_noncda$halibut, decreasing = T), ] %>% mutate(ordered = row_number())

# ggplot(ratio_noncda) +
#   geom_point(aes(yelloweye, halibut), alpha = 0.5) +
#   geom_point(data = ratio_cda, aes(yelloweye, halibut),
#     inherit.aes = F, colour = "red", alpha = 0.5) +
#   coord_cartesian(expand = F) +
#   ylab("Halibut per per 100 hooks") +
#   xlab("Yelloweye per per 100 hooks")

ggplot(ratio_noncda) +
  geom_point(aes(halibut, yelloweye), alpha = 0.5) +
  geom_point(
    data = ratio_cda, aes(halibut, yelloweye),
    inherit.aes = F, colour = "red", alpha = 0.5
  ) +
  coord_cartesian(expand = F) +
  xlab("Halibut biomass") +
  ylab("Yelloweye biomass")

# ggplot(filter(ratio_noncda, halibut > 5)) +
#   geom_histogram(aes(ye_per_hal)) +
#   geom_histogram(data = filter(ratio_cda, halibut > 5),aes(ye_per_hal), inherit.aes = F, fill = "red") +
#   ylab("Grid cell with estimate of > 5 halibut per 100 hooks") +
#   xlab("Predicted numder of yelloweye per halibut caught")

ggplot(filter(
  ratio_noncda, halibut > 0.1 # & yelloweye > 0.1
)) +
  geom_histogram(aes(hal_per_ye)) +
  geom_histogram(data = filter(
    ratio_cda, halibut > 0.1 # & yelloweye > 0.1
  ), aes(hal_per_ye), inherit.aes = F, fill = "red") +
  ylab("Cells with > 0.1 kg/ha of halibut") +
  xlab("Estimated ratio of kg halibut per kg yelloweye")
```

### Experiment with accumulation curve
Solid lines are cumulative halibut catch potential for each addition cell fished in decreasing order of predicted halibut abundance.
Dashed lines are the cumulative yelloweye catch that might be anticipated for those same cells.
```{r message=F, echo=F, warning=F}
ggplot(
  data = ratio_cda,
  aes(x = ordered)
) +
  geom_line(data = ratio_noncda, aes(x = ordered, y = cumsum((halibut))), inherit.aes = FALSE) +
  geom_line(data = ratio_cda, aes(x = ordered, y = cumsum((halibut))), colour = "red", inherit.aes = FALSE) +
  geom_line(data = ratio_noncda, aes(x = ordered, y = cumsum((yelloweye))), lty = 2, inherit.aes = FALSE) +
  geom_line(data = ratio_cda, aes(x = ordered, y = cumsum((yelloweye))), lty = 2, colour = "red", inherit.aes = FALSE) +
  coord_cartesian(expand = F, xlim = c(0, 2500), ylim = c(0, 2500)) +
  ylab("Fish biomass") +
  xlab("Number of cells fished (in order of decreasing Halibut abundance)")
```


# Investigate weights of yelloweye caught

### Is there an overall trend in fish size through time?

```{r message=F, echo=F}
# load biological sample data
yesampledata <- readRDS("data/yelloweye-surv-samples-all.rds") %>% filter(survey_abbrev == "HBLL OUT S")

# calculate mean weights for all of HBLL S
yemeanweights <- yesampledata %>%
  filter(!is.na(weight)) %>%
  group_by(year) %>%
  summarise(
    mean_weight = mean(weight / 1000, na.rm = T),
    upr_ci = Rmisc::CI(weight / 1000, ci = 0.95)[1], lwr_ci = Rmisc::CI(weight / 1000, ci = 0.95)[3],
    upr_weight = quantile(weight / 1000, 0.975), lwr_weight = quantile(weight / 1000, 0.025),
    n = n()
  )

# plot mean weights through time for whole HBLL
ggplot(yemeanweights) + geom_path(aes(year, mean_weight)) + ylim(0, 6) +
  geom_ribbon(aes(year, mean_weight, ymax = upr_weight, ymin = lwr_weight), alpha = 0.2) +
  geom_linerange(aes(year, ymax = upr_ci, ymin = lwr_ci), size = 1) +
  ylab("Individual Fish Weights (kg)") + xlab("Year") +
  ggtitle("Mean and 95th percentile range for Yelloweye Rockfish caught on HBLL S")
ggsave("annual_yelloweye_weights.png", width = 4, height = 4)
```


### Does the annual distribution of fish weights differ within the CDA?

```{r message=F, echo=F, warning=F}
# get the fishing events that occurred within CDA
d_ye_sf <- st_as_sf(d_ye, coords = c("longitude", "latitude"))
st_crs(d_ye_sf) <- 4326 # set the coordinate reference system
d_ye_intersected <- sf::st_intersects(d_ye_sf, focal_area)
cda_ye_sf <- d_ye_sf[which(lengths(d_ye_intersected) > 0), ]
noncda_ye_sf <- d_ye_sf[which(lengths(d_ye_intersected) == 0), ]

cda_ye_ids <- cda_ye_sf
st_geometry(cda_ye_ids) <- NULL
cda_ye_ids <- cda_ye_ids %>%
  select(fishing_event_id, year, catch_count) %>%
  distinct() # keep catch count for comparison with sample totals

# make dataframe of just samples from the CDA and calculate tallies of events, total catch, sampled weights and total catch/events
cda_ye_samples <- inner_join(cda_ye_ids, yesampledata) %>%
  group_by(year) %>%
  mutate(cda_weights = n())
cda_ye_catch <- cda_ye_ids %>%
  group_by(year) %>%
  summarise(cda_catch = sum(catch_count))
cda_ye_sample_sum <- cda_ye_samples %>%
  select(year, cda_weights) %>%
  distinct()
cda_events <- cda_ye_ids %>%
  group_by(year) %>%
  summarise(cda_events = n())
cda_sampling <- left_join(cda_events, cda_ye_catch) %>%
  left_join(cda_ye_sample_sum) %>%
  mutate(catch_rate = round(cda_catch / cda_events, 1))

# plot CDA weights against overall distribution for HBLL S
ggplot(yesampledata) +
  geom_violin(aes(as.factor(year), weight / 1000), alpha = 0.2, scale = "count", colour = "black", fill = "grey") +
  # geom_violin(data = cda_ye_samples, aes(as.factor(year), weight/1000), alpha = 0.9, scale = "count", colour = "red", fill = "red", adjust = 1/5) +
  geom_point(data = cda_ye_samples, aes(as.factor(year), weight / 1000), alpha = 0.7, colour = "red", fill = "red") +
  geom_linerange(data = yemeanweights, aes(as.factor(year), ymax = upr_ci, ymin = lwr_ci), size = 5) +
  ylab("Individual Fish Weights (kg)") + xlab("") +
  ggtitle("Annual distributions of Yelloweye Rockfish weights (all HBLL S = black; within CDA = red)")
ggsave("yelloweye_weights.png", width = 5, height = 3.5)
```



### How spatially variable are mean weigths through time for whole HBLL S?
```{r message=F, echo=F, warning=F}
# calculate the mean weights from each fishing event
yeeventweights <- yesampledata %>%
  filter(!is.na(weight)) %>%
  group_by(year, fishing_event_id) %>%
  summarise(
    mean_weight = mean(weight / 1000, na.rm = T),
    upr_ci = Rmisc::CI(weight / 1000, ci = 0.95)[1], lwr_ci = Rmisc::CI(weight / 1000, ci = 0.95)[3],
    upr_weight = quantile(weight / 1000, 0.975), lwr_weight = quantile(weight / 1000, 0.025),
    n = n()
  ) %>%
  filter(n > 10) # filter for fishing events with at least 10 fish measured

ggplot(yeeventweights) +
  geom_violin(aes(as.factor(year), mean_weight), alpha = 0.2, scale = "count", colour = "black", fill = "grey") +
  geom_linerange(data = yemeanweights, aes(as.factor(year), ymax = upr_ci, ymin = lwr_ci), size = 3) +
  ylab("Mean Weight (kg)") + xlab("") +
  ggtitle("Annual mean and variability in Yelloweye Rockfish weights", subtitle = "for events with > 10 fish sampled")
ggsave("yelloweye_event_weights.png", width = 6, height = 4.5)
```


```{r message=F, echo=F, warning=F}
yeeventweights1 <- yesampledata %>%
  filter(!is.na(weight)) %>%
  group_by(year, fishing_event_id) %>%
  summarise(
    mean_weight = mean(weight / 1000, na.rm = T),
    med_weight = median(weight / 1000, na.rm = T),
    upr_ci = Rmisc::CI(weight / 1000, ci = 0.95)[1], lwr_ci = Rmisc::CI(weight / 1000, ci = 0.95)[3],
    upr_weight = quantile(weight / 1000, 0.975), lwr_weight = quantile(weight / 1000, 0.025),
    n = n()
  ) %>%
  filter(n > 1)

ggplot(yeeventweights1) +
  geom_col(aes(med_weight, n), size = 2, colour = "grey") +
  # geom_linerange(data = yemeanweights, aes(as.factor(year), ymax = upr_ci, ymin = lwr_ci), size = 3) +
  ylab("Number of fish sampled") + xlab("Median weight of fish sampled (kg)") +
  # facet_wrap(~year) +
  ggtitle("")

ggplot(yeeventweights1) +
  geom_col(aes(mean_weight, n), size = 2, colour = "grey") +
  # geom_linerange(data = yemeanweights, aes(as.factor(year), ymax = upr_ci, ymin = lwr_ci), size = 3) +
  ylab("Number of fish sampled") + xlab("Mean weight of fish sampled (kg)") +
  # facet_wrap(~year) +
  ggtitle("")
```
