---
title: "Create filled in prediction grid with RCAs excluded"  
author:
- Philina A. English
- Lindsay N.K. Davidson
date: "21 July 2021"
---

#Purpose  

This code is to create a filled in prediction grid for southern outside Hard Bottom Longline survey area. The prediction grid is a 2 km X 2 km grid that extends from 20m to the 1000m bathymetry within this zone and excludes RCAs. 

```{r setup, include = FALSE, cache=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE, message = FALSE, warning = FALSE, evaluate = FALSE, cache = TRUE
)
```


```{r packages, include = FALSE, evaluate = FALSE}
library(sf)
library(sp) #coverting to UTMS
library(rgdal) #converting to UTMS
library(PBSmapping) #depth contours
library(maptools)
library(rgeos)
library(here)
library(tidyverse)
library(raster)
# install.packages("marmap") # needs to be installed but not loaded 
```


To create the grid, I first created bounding boxes to accomodate the strange shape of the grid more closely. 
The west and east limits were defined by the 1000 m bathymetry [bathymetry data from `PBSmapping` (Schnute, Boers, and Haigh, 2021)] and shoreline [spatial data from Hakai Institute]. 
The prediction grid covered the extent of the bounding box and was a 2 km X 2 km resolution. 
The final database comprised of the locations of the centroids for each of the 2 km X 2 km grid cells.  

Load HBLL grid
```{r loaddat, include = FALSE}
hbll_s_grid <- readRDS(here::here("grids/hbll_s_grid.rds"))
```

Use bathymetry contours from PBSmapping to define grid area
```{r bathymetry, include = FALSE }
sp_dat1 <- hbll_s_grid$grid %>% filter(latitude < 50.5) #%>% select(x, y)
sp_dat2 <- hbll_s_grid$grid %>% filter(latitude > 50.5) 

## Create the clipping polygons
CP <- as(raster::extent(
  min(hbll_s_grid$grid$x)-1000, max(hbll_s_grid$grid$x)+1000,
  min(hbll_s_grid$grid$y)-1000, max(hbll_s_grid$grid$y)+1000
  ), "SpatialLines")

CP1 <- as(raster::extent(
  min(sp_dat1$x), max(sp_dat1$x),
  min(sp_dat1$y), max(sp_dat1$y)
  ), "SpatialLines")

CP2 <- as(raster::extent(
  min(sp_dat2$x), max(sp_dat2$x),
  min(sp_dat2$y), max(sp_dat2$y)
  ), "SpatialLines")

crsstring <- "+proj=utm +zone=9 +datum=NAD83 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0  +units=m +no_defs" # i believe this is 3156
crsnum <- 3156

proj4string(CP) <- CRS(crsstring) 
proj4string(CP1) <- CRS(crsstring) 
proj4string(CP2) <- CRS(crsstring) 
CP <- st_as_sf(CP)
CP1 <- st_as_sf(CP1)
CP2 <- st_as_sf(CP2)
CP <- st_transform(CP, crs = crsnum)
CP1 <- st_transform(CP1, crs = crsnum)
CP2 <- st_transform(CP2, crs = crsnum)

#use this polygon and clip to the contours in bcBathymetry
# citation("PBSmapping")
data(bcBathymetry) #bathymetry
contour(bcBathymetry$x, bcBathymetry$y, bcBathymetry$z, col = "pink", method = "edge", vfont = c("sans serif", "plain"))
#,   nlevels = 2)
#make a spatial object
cont <- contourLines(bcBathymetry$x, bcBathymetry$y, bcBathymetry$z, nlevels = 1000) 
# class(cont)
#generate contours
clines <- ContourLines2SLDF(cont)
clines@data[["level"]]
lines <- st_as_sf(clines) #make sf object

# SHALLOW BOUNDARY
c.linesfilter <- lines %>% filter(level == 20) 
st_crs(c.linesfilter) <- CRS('+proj=longlat')
c.linesproj <- st_transform(c.linesfilter, crs = crsnum)
gridarea <- st_bbox(st_intersection(st_geometry(CP1), st_geometry(c.linesproj))) %>% st_point %>% st_sfc(crs=3156)
sa_clip <- st_intersection(st_as_sfc(st_bbox(CP1)),c.linesproj)

#DEEP BOUNDARY
c.linesfilter2 <- lines %>% filter(level == 1000) 
st_crs(c.linesfilter2) <- CRS('+proj=longlat')
c.linesproj2 <- st_transform(c.linesfilter2, crs = crsnum)
gridarea2 <- st_bbox(st_intersection(st_geometry(CP1), st_geometry(c.linesproj2))) %>% st_point %>% st_sfc(crs=3156)
sa_clip2 <- st_intersection(st_as_sfc(st_bbox(CP1)),c.linesproj2)

# SHALLOW BOUNDARY IN NORTH
c.linesfilter <- lines %>% filter(level == 20) 
st_crs(c.linesfilter) <- CRS('+proj=longlat')
c.linesproj <- st_transform(c.linesfilter, crs = crsnum)
gridarea <- st_bbox(st_intersection(st_geometry(CP2), st_geometry(c.linesproj))) %>% st_point %>% st_sfc(crs=3156)
sa_clipN <- st_intersection(st_as_sfc(st_bbox(CP2)),c.linesproj)

#DEEP BOUNDARY IN NORTH
c.linesfilter2 <- lines %>% filter(level == 1000) 
st_crs(c.linesfilter2) <- CRS('+proj=longlat')
c.linesproj2 <- st_transform(c.linesfilter2, crs = crsnum)
gridarea2 <- st_bbox(st_intersection(st_geometry(CP2), st_geometry(c.linesproj2))) %>% st_point %>% st_sfc(crs=3156)
sa_clipN2 <- st_intersection(st_as_sfc(st_bbox(CP2)),c.linesproj2)

ggplot() +
  # geom_sf(data=st_as_sfc(st_bbox(CP1)),fill=NA) +
  geom_sf(data=sa_clip) +
  geom_sf(data=sa_clip2) +
  geom_sf(data=sa_clipN) +
  geom_sf(data=sa_clipN2) +
  theme_classic()

#Cast the linestring to points, append the corner, close the linestring, turn into polygon.
pts_shallow <- sa_clip %>% st_geometry %>% st_cast("POINT")
pts_deep <- sa_clip2 %>% st_geometry %>% st_cast("POINT")
pts_shallowN <- sa_clipN %>% st_geometry %>% st_cast("POINT")
pts_deepN <- sa_clipN2 %>% st_geometry %>% st_cast("POINT")
# 
# st_bbox(pts_shallow) <- st_bbox(CP) 

corner <- st_bbox(CP2)[c('xmin','ymax')] %>% st_point %>% st_sfc(crs=crsnum)%>% st_cast("POINT")

# test <- st_intersection(CP1, pts) %>% st_geometry %>% st_cast("POINT")
sa_lineN <- c(pts_shallowN[1:195], pts_deepN[1:90], 
  corner, pts_shallowN[1]) %>% st_combine %>% st_cast('LINESTRING')
sa_lineS <- c(pts_shallow[1:218], pts_deep[1:212], pts_shallow[1]) %>% st_combine %>% st_cast('LINESTRING')
# sa_polyN <- c(pts_shallowN[1:195], pts_deepN[1:90], corner, 
#   pts_shallowN[1]
#   ) %>% st_combine %>% st_cast('LINESTRING') %>% st_polygonize()
# sa_polyS <- c(pts_shallow[1:218], pts_deep[1:212], pts_shallow[1]
#   ) %>% st_combine %>% st_cast('LINESTRING') %>% st_polygonize()
sa_poly <-  c(
  pts_shallowN[1:195], pts_shallow[1:218],
  pts_deep[1:212], pts_deepN[1:90],
  corner, pts_shallowN[1]
  ) %>% st_combine %>% st_cast('LINESTRING') %>% st_polygonize()

ggplot() +
  # geom_sf(data=sa_lineN) +
  # geom_sf(data=sa_lineS) +
  geom_sf(data=sa_poly) +
  # coord_sf(xlim = st_bbox(CP)[c(1,3)], # min & max of x values
  #          ylim = st_bbox(CP)[c(2,4)]) +
  theme_classic()
```

Create grid cells to fill in grid area
```{r}
grid1 <- sf::st_make_grid(x = sa_poly,
  offset = c(-1000, 1000),
  cellsize=c(2000, 2000))

keep <- st_intersects(sa_poly, grid1)
grid1 <- grid1[unlist(keep)]

new_grid <- st_as_sf(grid1)

ggplot() +
  # geom_sf(data=sa_poly) +
  # geom_sf(data=grid1) +
  geom_sf(data=new_grid) +
  theme_classic()
```


```{r eval=FALSE}
## Add in trawl grid -- turns out it all falls within the above so this step not needed/completed
# trawl <- readRDS(here::here("grids/nd_all_synoptic_new.rds")) %>% 
#   mutate(#X = round(X), Y = round(Y),
#     # X = X / 100, Y = Y / 100,
#     X = X*1000, Y = Y*1000,
#     depth_m = depth
#   ) %>% select(X, Y, depth_m) #%>%
#   # filter(
#   #   X > min(hbll_s_grid$grid$X) & X < max(hbll_s_grid$grid$X) &
#   #     Y > min(hbll_s_grid$grid$Y) & Y < max(hbll_s_grid$grid$Y)
#   # )
# 
# min(trawl$X)
# max(trawl$X)
# 
# trawl_sf <- st_as_sf(trawl, coords = c("X", "Y"), crs = 3156)
# trawl_sf_grid <- sf::st_make_grid(x = trawl_sf,
#   offset = st_bbox(trawl_sf)[c("xmin", "ymin")]+ c(-1000, -1000),
#   cellsize=c(2000, 2000))
# 
# keep <- st_intersects(trawl_sf, trawl_sf_grid)
# trawl_sf_grid <- trawl_sf_grid[unlist(keep)]
# trawl_sf2 <- st_as_sf(trawl_sf_grid)
# trawl_sf2$source_data <- "TRAWL"
# 
# ggplot() +
#   geom_sf(data=new_grid, colour = "red") +
#   geom_sf(data=trawl_sf2, alpha = 0.5, colour ="NA") +
#   theme_classic()

# 
# # grid_utm <- full_join(grid, s_grid_utm, by = c("X", "Y")) %>%
# #   mutate(depth = ifelse(is.na(depth_m), depth, depth_m), 
# #     survey = ifelse(is.na(survey), "TRAWL" #survey2
# #       , survey)) %>%
# #   select(-depth_m, #-survey2, 
# #     -latitude, -longitude)
# # 
# # grid_xy <- grid_utm %>%
# #   select(X, Y) %>%
# #   mutate(X = X * 100, Y = Y * 100)
# # grid_ll <- utm2ll(grid_xy) %>% rename(longitude = X, latitude = Y)
# # 
# # grid_utm <- bind_cols(grid_utm, grid_ll)
# # 
# # grid_sf <- st_as_sf(grid_utm, coords = c("longitude", "latitude"))
# # st_crs(grid_sf) <- 4326 # set the coordinate reference system
# # grid <- sfc_as_cols(grid_sf, c("longitude", "latitude"))
# # st_geometry(grid) <- NULL
# # 
# # saveRDS(grid, file = "data-generated/hybrid_grid.rds") 
```

Remove Rockfish Conservation Areas (RCAs) from grid
```{r}
# get RCA
rcas <- st_read(here::here("grids/RCA2019/RCA_2019.shp"))
## plot(rcas) # takes an impossivbly long time so do not do!
# glimpse(rcas)

rcas_utm <- st_transform(rcas, crs = 3156) # convert to utm proj used for grid
# rcas_ll <- st_transform(rcas, crs = 4326) # if needed in lat lon

cells_in_rcas <- st_intersection(new_grid, rcas_utm)
rcas_in_grid <- st_intersection(rcas_utm, new_grid)

# plot(rcas_in_grid)

# this approach of getting centroids fails... none of cell centroids seem to match
# cells_in_rcas$geometry <- st_centroid(cells_in_rcas) %>% st_geometry()
# coords_rcas <- as.data.frame(st_coordinates(cells_in_rcas$geometry))

#not sure why, but st_union required otherwise df becomes huge!
new_grid_norca <- st_difference(new_grid, st_union(cells_in_rcas))

# new_grid_norca <- st_difference(new_grid, st_union(rcas_in_grid))

# st_is_valid(new_grid)
# st_is_valid(cells_in_rcas)
# class(new_grid)
# class(cells_in_rcas)
# st_erase = function(x, y) st_difference(x, st_union(st_combine(y)))

# new_grid_norca <- st_erase(new_grid, cells_in_rcas)
# rca_keep <- st_intersects(new_grid, rcas_utm)
# cells_in_rcas <- rcas_utm[unlist(rca_keep)]
# cells_in_rcas <- st_as_sf(cells_in_rcas)

saveRDS(new_grid_norca, here::here("grids/hbll_shp_grid_norca.rds"))

ggplot() +
  geom_sf(data=new_grid_norca) +
  theme_classic()
```

Make dataframe with UTMs and lat lons
```{r}
new_grid_utm <- new_grid_norca # already in UTMs

new_grid_utm$area <- as.numeric(st_area(new_grid_utm))
new_grid_utm$geometry <- st_centroid(new_grid_utm) %>% st_geometry()
hbll_s_grid_utm <- as.data.frame(st_coordinates(new_grid_utm$geometry))
hbll_s_grid_utm$area <- new_grid_utm$area 
hbll_grid_utm <- dplyr::select(hbll_s_grid_utm, area, X, Y) %>%
  rename(x = X, y = Y) %>% mutate(X = round(x/1000)/100, Y = round(y/1000)/100)

new_grid_ll <- st_transform(new_grid_norca, crs = 4326)
new_grid_ll$geometry <- st_centroid(new_grid_ll) %>% st_geometry()
hbll_s_grid_ll <- as.data.frame(st_coordinates(new_grid_ll$geometry))
hbll_grid_ll <- dplyr::select(hbll_s_grid_ll, X, Y) %>%
  rename(longitude = X, latitude = Y)

# cells_to_remove <- dplyr::select(coords_rcas, X, Y) %>%
#   rename(x = X, y = Y) %>% mutate(X = round(x/1000)/100, Y = round(y/1000)/100)

new_grid_norca  <- bind_cols(hbll_grid_ll, hbll_grid_utm)# %>% filter(area > 2e+06)

ggplot(new_grid_norca) +
  geom_tile(aes(X,Y, width = sqrt(area)/100000, height = sqrt(area)/100000))+
  theme_classic()

# hbll_grid %>% mutate(X = round(X * 100), Y = round(Y * 100)) %>%
#   mutate(X = (X / 100), Y = (Y / 100)) %>% View()
```

Check if range of old and new grids match after rounding
```{r}
new_grid_norca 

old_grid <- readRDS(here::here("grids/hbll_s_grid.rds"))
old_grid <- old_grid$grid %>% mutate(X = round(X * 100), Y = round(Y * 100)) %>%
  mutate(X = (X / 100), Y = (Y / 100))

range(old_grid$X)
range(new_grid_norca$X)

range(old_grid$Y)
range(new_grid_norca$Y)

if(all(c(range(old_grid$X),range(old_grid$Y)) == c(range(new_grid_norca$X),range(new_grid_norca$Y))) ){
saveRDS(new_grid_norca, here::here("grids/hbll_s_grid_norca.rds"))
}
```


# Get depth data for all grid cells

Download depth data for extent of new grid
```{r}
f <- "data/bath_res1_marmap.rds"
if(!file.exists(f)){
# Load package
library(marmap)
new_grid_norca <- readRDS(here::here("grids/hbll_s_grid_norca.rds"))
# Download bathymetric data and save on disk
bat <- getNOAA.bathy(min(new_grid_norca$longitude)-2, max(new_grid_norca$longitude)+2,
  min(new_grid_norca$latitude)-2, max(new_grid_norca$latitude)+2, res = 1, keep = TRUE) #resolution of the grid, in minutes (default is 4 or > 4 miles)
saveRDS(bat, "data/bath_res1_marmap.rds")
}
```

Explore depth data retrieved
```{r eval=F}
# Load package
library(marmap)
bat <- readRDS(here::here("data/bath_res1_marmap.rds"))
# Create nice looking color palettes
blues <- c("lightsteelblue4", "lightsteelblue3", "lightsteelblue2", "lightsteelblue1")
greys <- c(grey(0.6), grey(0.93), grey(0.99))
# Plot
plot(bat, image = TRUE, land = TRUE, lwd = 0.1, bpal = list(c(0, max(bat), greys), c(min(bat), 0, blues)))
plot(bat, lwd = 0.8, deep = -1000, shallow = -20, step = 20, add = TRUE) # highlight coastline

# Get depth profile along both tracks and remove positive depths (since random fake values can be on land)
# path.profile() gets depth value for all cells of the bathymetric grid below the gps tracks
path1 <- path.profile(track1[,-3], bat) ; path1 <- path1[-path1[,4]>0,]
path2 <- path.profile(track2[,-3], bat) ; path2 <- path2[-path2[,4]>0,]
# Get depth values for each gps tracking point
# get.depth() retrieve depth values only for gps tracking points
depth1 <- get.depth(bat, track1$lon, track1$lat, locator = FALSE, distance = TRUE) ;
depth2 <- get.depth(bat, track2$lon, track2$lat, locator = FALSE, distance = TRUE) ;
# Add depth values to tracks 1 and 2 and remove positive depths
track1$depth <- depth1$depth ; track1 <- track1[-track1$depth > 0,]
track2$depth <- depth2$depth ; track2 <- track2[-track2$depth > 0,]
# Plot
layout(matrix(c(1, 2, 1, 3, 4, 4), ncol = 2, byrow = TRUE), height = c(1, 1, 1))
## Bathymetric map with gps tracks
plot(bat, land = TRUE, image = TRUE, lwd = 0.2, bpal = list(c(min(bat,na.rm=TRUE), 0, blues), c(0, max(bat, na.rm=TRUE), greys)), ylim=c(-36.5,-35.25))
plot(bat, deep = 0, shallow = 0, step = 0, lwd = 0.8, add = TRUE)
lines(track1, col = "brown3")
lines(track2, col = "darkorange1")
legend("topright", legend = c("Track 1", "Track 2"), lwd = 1, col = c("brown3", "darkorange1"), pch = 1, pt.cex = 0.5, bg="white")
## Depths profiles along gps tracks
plotProfile(path1, main = "Track 1")
plotProfile(path2, main = "Track 2")
## Depth as a function of time since the deployment of gps tags
par(mar=c(5,4,1,2))
plot(track1$time, track1$depth, xlab = "Time (arbitrary unit)", ylab = "Depth (m)", type = "o", cex = 0.5, col = "brown3", xlim = range(c(track1$time, track2$time)), ylim = range(c(track1$depth, track2$depth)))
lines(track2$time, track2$depth, type = "o", cex = 0.5, col = "darkorange1")
legend("bottomright", legend = c("Track 1", "Track 2"), lwd = 1, col = c("brown3", "darkorange1"), pch = 1, pt.cex = 0.5)
```

Extract depth for grid cells
```{r}
# make depth raster
bat <- readRDS(here::here("data/bath_res1_marmap.rds"))
rast_bat <- marmap::as.raster(bat) 

# change projection to match grid
proj <- "+proj=utm +zone=9 +datum=NAD83 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0  +units=m +no_defs"
rast_bat <- projectRaster(rast_bat, crs = proj) 
plot(rast_bat)

# depth for complete cells only
hbll_grid <- readRDS(here::here("grids/hbll_s_grid_norca.rds"))
grid_scale <- 2000 #scale of prediction grid in m
grid <- raster(
  ext = extent(hbll_grid)+c(-1000, 1000, -1000, 1000), # need to add 1km in all directions to allow coordinates to be the centroids of 2x2km cells
  resolution = grid_scale, crs = CRS(proj))

grid.df <- as.data.frame(grid, xy = TRUE)
grid.df$layer <- NULL
depth <- raster::extract(x=rast_bat, y=grid.df, fun = mean, na.rm = T, exact=T)
extracted_depth <- cbind(grid.df, depth)

hbll_grid_full_cells <- left_join(hbll_grid, extracted_depth)

# depth for partial cells too
new_grid_norca <- readRDS(here::here("grids/hbll_shp_grid_norca.rds"))
new_grid_norca <- st_as_sf(new_grid_norca)
new_grid_norca <- st_transform(new_grid_norca, crs = 3156)

# unweighted depths
get_depth <- raster::extract(x=rast_bat, y=new_grid_norca, na.rm = T, exact=T, sp = T)
mean_depth <- unlist(lapply(get_depth, function(x) if (!is.null(x)) mean(x, na.rm=TRUE) else NA ))

# weighted depths
get_depth2 <- raster::extract(x=rast_bat, y=new_grid_norca, na.rm = T, exact=T, weights=T, sp = T)
mean_depth2 <- sapply(get_depth2, function(x) if (!is.null(x)) {sum(apply(x, 1, prod)) / sum(x[,2])} else NA)


all_depths <- bind_cols(hbll_grid_full_cells, mean_depth = mean_depth, wm_depth = mean_depth2) %>% 
  mutate(cell_depth = -depth, depth_uw = -mean_depth, depth_wm = -wm_depth, depth = -wm_depth) %>% dplyr::select(-mean_depth, -wm_depth)

saveRDS(all_depths, here::here("grids/exrtracted_depths_norca.rds"))


ggplot(all_depths) + geom_point( aes(cell_depth, depth_uw, colour = area),alpha=0.2) # unweighted
ggplot(all_depths) + geom_point( aes(cell_depth, depth_wm, colour = area), alpha=0.2) # weighted
# weighted seems closer to the full cells only way of doing this...
ggplot(all_depths) + geom_point(aes(depth_wm, depth_uw, colour = area),alpha=0.2)

# will apply this filter after extracting substrate
hbll_grid_keep <- all_depths %>%
  # filter(depth_all < 1100) %>% filter(depth_all > 10) 
  filter(depth > 0.5) 

# ggplot(all_depths) +
ggplot(hbll_grid_keep) +
  geom_point(aes(X,Y, colour = log(depth)), alpha = 0.75) +
  scale_colour_viridis_c(direction = -1) +
  # geom_point(aes(X,Y, colour = -cell_depth), alpha = 0.2) +
  theme_classic()
```

# Get substrate covariates

Convert tif projection and save as high res rasters
```{r}
f <- "data/highres-sandy-raster.grd" 
if (!file.exists(f)) {
# retrieve substate layers if not done so before
rocky <- raster("data/substrate/rocky.tif")
mixed <- raster("data/substrate/mixed.tif")
muddy <- raster("data/substrate/muddy.tif")
sandy <- raster("data/substrate/sandy.tif")

# original projection
proj <- "+proj=aea +lat_1=50 +lat_2=58.5 +lat_0=45 +lon_0=-126 +x_0=1000000 +y_0=0"
projdefs <- "+datum=NAD83 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"
geoCRS <- paste( proj, projdefs, sep=" " )

# new projection
proj <- "+proj=utm +zone=9 +datum=NAD83 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0  +units=m +no_defs"

new_rocky <- raster::projectExtent(rocky, crs = proj)
raster::res(new_rocky) <- 100
new_mixed <- raster::projectExtent(mixed, crs = proj)
raster::res(new_mixed) <- 100
new_muddy <- raster::projectExtent(muddy, crs = proj)
raster::res(new_muddy) <- 100
new_sandy <- raster::projectExtent(sandy, crs = proj)
raster::res(new_sandy) <- 100

# # Project values to new raster
hres_rocky <- raster::projectRaster(rocky, new_rocky) #, method = "ngb")
writeRaster(hres_rocky, file = "data/highres-rocky-raster.grd")
hres_mixed <- raster::projectRaster(mixed, new_mixed) #, method = "ngb")
writeRaster(hres_mixed, file = "data/highres-mixed-raster.grd")
hres_muddy <- raster::projectRaster(muddy, new_muddy) #, method = "ngb")
writeRaster(hres_muddy, file = "data/highres-muddy-raster.grd")
hres_sandy <- raster::projectRaster(sandy, new_sandy) #, method = "ngb")
writeRaster(hres_sandy, file = "data/highres-sandy-raster.grd")
}
```

Extract variables for new grid
```{r}
# load previously saved raster
rocky <- raster("data/highres-rocky-raster.grd")
## with weights
get_rocky2 <- raster::extract(x=rocky, y=new_grid_norca, na.rm = T, exact=T, weights=T, sp = T)
mean_rocky2 <- sapply(get_rocky2, function(x) if (!is.null(x)) {sum(apply(x, 1, prod), na.rm = T) / sum(x[,2], na.rm = T)} else NA)
## without weights
# get_rocky <- raster::extract(x=rocky, y=new_grid_norca, na.rm = T, exact=T, sp = T)
# mean_rocky <- unlist(lapply(get_rocky, function(x) if (!is.null(x)) mean(x, na.rm=TRUE) else NA ))

muddy <- raster("data/highres-muddy-raster.grd")
## with weights
get_muddy <- raster::extract(x=muddy, y=new_grid_norca, na.rm = T, exact=T, weights=T, sp = T)
mean_muddy <- sapply(get_muddy, function(x) if (!is.null(x)) {sum(apply(x, 1, prod), na.rm = T) / sum(x[,2], na.rm = T)} else NA)
## without weights
# get_muddy <- raster::extract(x=muddy, y=new_grid_norca, na.rm = T, exact=T, sp = T)
# mean_muddy <- unlist(lapply(get_muddy, function(x) if (!is.null(x)) mean(x, na.rm=TRUE) else NA ))

mixed <- raster("data/highres-mixed-raster.grd")
get_mixed <- raster::extract(x=mixed, y=new_grid_norca, na.rm = T, exact=T, weights=T, sp = T)
mean_mixed <-  sapply(get_mixed, function(x) if (!is.null(x)) {sum(apply(x, 1, prod), na.rm = T) / sum(x[,2], na.rm = T)} else NA)
## or without weights
# get_mixed <- raster::extract(x=mixed, y=new_grid_norca, na.rm = T, exact=T, sp = T)
# mean_mixed <- unlist(lapply(get_mixed, function(x) if (!is.null(x)) mean(x, na.rm=TRUE) else NA ))

sandy <- raster("data/highres-sandy-raster.grd")
get_sandy <- raster::extract(x=sandy, y=new_grid_norca, na.rm = T, exact=T, weights=T, sp = T)
mean_sandy <-  sapply(get_sandy, function(x) if (!is.null(x)) {sum(apply(x, 1, prod), na.rm = T) / sum(x[,2], na.rm = T)} else NA)

# add substrate to grid with depth data
all_covs <- bind_cols(all_depths, rocky = mean_rocky2, rocky_uw = mean_rocky, muddy = mean_muddy, mixed = mean_mixed, sandy = mean_sandy) 

# check how weighting changes things?
ggplot(all_covs) +
  geom_point(aes(rocky, rocky_uw, colour = log(area)), alpha = 0.25) +
  theme_classic()

saveRDS(all_covs, "norca_grid_w_substrate.rds")
```



